### 2022-07-05 iclfs_review/lit_review.Rmd
Add literature review markdown file

---
title: The aspects of integrated crop-livestock-forest system in Brazil

author: Hugo Tameirão Seixas

output:
  html_document:
    theme: readable
    number_sections: true

---

# Title and Abstract

# Aims and questions

# Review registration

# Eligibility criteria

# Finding studies

## Define the type of search (e.g.comprehensive search, representative sample)

## State what sources of information were sought (e.g. published and unpublished studies, personal communications)

## Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators

Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril)

Embrapa: (ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)

## Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)

# Study selection

# Data collection process

# Data items

# Assessment of individual study quality

# Effect size measures

# Missing data

# Meta-analytic model description

# Software

# Non independence

# Meta-regression and model selection

# Publication bias and sesitivity analysis

# Clarification of post hoc analysis

# Metadata data and code

# Results of study selection process

# Sample sizes and study characteristics

# Meta-analysis

# Heterogeneity

# Meta-regression

# Outcomes of publication bias and sensitivity analyses

# Discussion

# Contributions and funding

# References

### 2022-07-05 iclfs_review/naive_search.R
Delete code and files that will not be used anymore

@@ -1,159 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:        Perform Naive Literature Search
-# Description:  This script perform a naive search for literature regarding
-#               Integrated Crop Livestock Forestry Systems of production in
-#               the scopus database. The title, keywords and abstract section
-#               from documents found in the search are analysed to find new
-#               keywords related to the subject of interest. Keywords are
-#               than saved in a csv table for further analysis.
-#
-# Author:       Hugo Tameirao Seixas
-# Contact:      tameirao.hugo@gmail.com
-# Date:         2021-03-16
-#
-# Notes:
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(fulltext)
-library(tidytext)
-library(stopwords)
-library(glue)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-stop_words <- # A list of words we want to avoid in our exploration
-  tibble(
-    word = c(
-      stopwords::stopwords(language = "pt"),
-      stopwords::stopwords(language = "en")
-    )
-  )
-#
-# NAIVE SEARCH ----------------------------------------------------------------
-
-## Set keywords for naive search ----
-naive_keywords <-
-  c( # Very specific set of words
-    "iclfs",
-    "crop-livestock-forestry",
-    "crop-livestock-forest",
-    "lavoura-pecuária-floresta"
-  )
-
-## Create naive query ----
-naive_query <-
-  glue( # We search for our words in the title, abstract and keywords sections
-    "TITLE-ABS-KEY({glue_collapse(naive_keywords, sep = ' OR ')})"
-  )
-
-## Search in Scopus ----
-scopus_naive <-
-  scopus_search_loop(
-    query = naive_query,
-    type = "search",
-    view = "COMPLETE",
-    count = 300
-  )
-
-## Transform to tibble and select columns ----
-naive_results_table <-
-  scopus_naive$results %>%
-  as_tibble() %>%
-  select(
-    scopus_id = `dc:identifier`, title = `dc:title`,
-    abstract = `dc:description`, keywords = `authkeywords`
-  )
[…]

### 2022-07-05 iclfs_review/search_and_download.R

@@ -1,77 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:        Perform Literature Search and Download Documents
-# Description:
-#
-# Author:       Hugo Tameirao Seixas
-# Contact:      tameirao.hugo@gmail.com
-# Date:         2021-03-18
-#
-# Notes:
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(fulltext)
-library(glue)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-
-#
-# LOAD AND CLEAN NAIVE KEYWORDS -----------------------------------------------
-
-naive_keywords_classes <-
-  read_csv("iclfs_review/naive_keywords_classes.csv") %>%
-  filter(group != 0) # Remove useless keywords
-
-# LITERATURE SEARCH -----------------------------------------------------------
-
-## Get keywords and create query ----
-
-### Filter keywords ----
-keywords <- naive_keywords_classes %>%
-  filter(group == 1) %>% # Our search will be performed using group 1
-  pull(word)
-
-### Concatenate words with OR statement ----
-iclfs_query <- glue_collapse(keywords, sep = '" OR "')
-
-### Create query ----
-iclfs_query <- glue('TITLE-ABS-KEY("{iclfs_query}")')
-
-## Search documents in Scopus ----
-
-### Core search ----
-iclfs_search <-
-  scopus_search(query = iclfs_query,content = "core")
-
-### Get total numbrs of found documents ----
-total_results <-
-  as.numeric(iclfs_search$`search-results`$`opensearch:totalResults`)
-
-### Get the results ----
-iclfs_search <-
-  scopus_search_loop(
-    query = iclfs_query,
-    type = "search",
-    view = "STANDARD",
-    count = total_results
-  )
-
-## Transform to tibble and select columns ----
-iclfs_results <-
-  iclfs_search$results %>%
-  as_tibble() %>%
-  select(
-    title = `dc:title`, doi = `prism:doi`,
-    `affiliation`, date = `prism:coverDate`
-  )
-
-## Download documents ----
-
-### Set path to save documents ----
-cache_options_set(full_path = "iclfs_review/bib/")
-
-### Perform download ----
-walk(iclfs_results$doi, ~ { try(ft_get(.x, type = "pdf")) })

### 2022-07-07 iclfs_review/lit_review.Rmd
Wrote some aims of the review

@@
 # Aims and questions
+
+## Provide a rationale for the review
+
+## Reference any previous reviews or meta-analyses on the topic
+
+## State the aims and scope of the review (including its generality)
+
+In this review I will analyse studies about ICLFS in Brazil. I pretend to answer several questions:
+
+- Where are experiments on ICLFS being conducted?
+
+- What are the characteristics of these systems? (species used, fertilizers, number of individuals per hectare, duration of the production cycle...)
+
+- What are the fiber and food productivity in these systems?
+
+- What is the amount of above ground carbon (alive and dead) being accumulated?
+
+- What is the amount of below ground carbon being accumulated?
+
+- What are the emissions of green house gases related to the ICLFS?
+
+- What is the economic revenue from the adoption of the ICLFS?
+
+## State the primary questions the review addresses (e.g. which moderators were tested)
+
+## Describe whether effect sizes were derived from experimental and/or observational comparisons
 

### 2022-07-08 iclfs_forms/form.R
Add ideas for new questions

@@ -252,12 +252,85 @@ ui <-
 
       ## Question 06: ----
       tabPanel(
-        "Question 06"
+        "Question 06",
+        sidebarLayout(
+          sidebarPanel( # Inputs panel
+            width = 10,
+            titlePanel(
+              title = "Perfil do especialista: anos de experiencia, local de
+              experiencia"
+            )
+          ),
+          mainPanel( # Outputs panel
+
+          )
+        )
       ),
 
       ## Question 07: ----
       tabPanel(
-        "Question 07"
+        "Question 07",
+        sidebarLayout(
+          sidebarPanel( # Inputs panel
+            width = 10,
+            titlePanel(
+              title = "Quanto tempo dura a transição para o ILPF?
+              Como ela é feita?"
+            )
+          ),
+          mainPanel( # Outputs panel
+
+          )
+        )
+      ),
+
+      ## Question 08: ----
+      tabPanel(
+        "Question 08",
+        sidebarLayout(
+          sidebarPanel( # Inputs panel
+            width = 10,
+            titlePanel(
+              title = "Quais são os insumos utilizados? Quanto?"
+            )
+          ),
+          mainPanel( # Outputs panel
+
+          )
+        )
+      ),
+
+      ## Question 09: ----
+      tabPanel(
+        "Question 09",
+        sidebarLayout(
+          sidebarPanel( # Inputs panel
+            width = 10,
+            titlePanel(
+              title = "Qual a área média de um ilpf?"
+            )
+          ),
+          mainPanel( # Outputs panel
+
+          )
+        )
+      ),
+
+      ## Question 10: ----
+      tabPanel(
+        "Question 10",
+        sidebarLayout(
+          sidebarPanel( # Inputs panel
+            width = 10,
+            titlePanel(
+              title = "Quais serviços ecossistêmicos
+              estão relacionados ao ILPF?"
+            )
+          ),
+          mainPanel( # Outputs panel
+
+          )
+        )
       ),
 
       ## Submission ----

### 2022-07-08 iclfs_projections/model.R
Add code header. Add new variables to the model. Delete code that wont be used.

@@ -1,13 +1,36 @@
-
+# HEADER ----------------------------------------------------------------------
+#
+# Title:
+# Description:
+#
+#
+#
+# Authors:      Hugo Tameirao Seixas
+# Contact:      tameirao.hugo@gmail.com
+# Date:         2022-07-07
+#
+# Notes:
+#
+#
+#
+#
+#
+# LIBRARIES -------------------------------------------------------------------
+#
 library(terra)
 library(tidyverse)
+#
+# OPTIONS ---------------------------------------------------------------------
+#
+#
+# LOAD BASE GRID --------------------------------------------------------------
 
+## Load raster file
 r <- rast("iclfs_projections/base_grid_pasture.tif")
 
-# Calculate a linear expansion rate
-annual_increase <- floor(pull(global(r, sum, na.rm = TRUE) / 30))
+# GENERATE RANDOM DATA AS DUMMIES ---------------------------------------------
 
-# Generate random system types to be sampled
+## Generate random system types to be sampled
 systems <-
   reduce(
     map2(
@@ -17,7 +40,7 @@ systems <-
     c
   )
 
-# Generate random cycle lengths to be sampled
+## Generate random cycle lengths to be sampled
 cycle <-
   reduce(
     map2(
@@ -27,7 +50,7 @@ cycle <-
     c
   )
 
-# Generate random transition system type to be sampled
+## Generate random transition system type to be sampled
 transition_systems <-
   reduce(
     map2(
@@ -37,7 +60,7 @@ transition_systems <-
     c
   )
 
-# Generate random transition lengths to be sampled
+## Generate random transition lengths to be sampled
 transition_length <-
   reduce(
     map2(
@@ -47,8 +70,39 @@ transition_length <-
     c
   )
 
+## Generate random trees population/ha to be sampled
+tree_pop <-
+  reduce(
+    map2(
+      .x = c(333, 476, 370, 690, 715),
+      .y = sample(1:40, 5, replace = TRUE),
+      .f = ~ { rep(.x, .y) }),
+    c
+  )
 
-# Get degraded pasture from raster file and transform into a data frame
+## Generate ICLFS management to be sampled
+system_management <-
+  reduce(
+    map2(
+      .x = c(1, 2, 3, 4, 5),
+      .y = sample(1:40, 5, replace = TRUE),
+      .f = ~ { rep(.x, .y) }),
+    c
+  )
+
[…]

### 2022-07-25 iclfs_review/review_data_manager.R
Add dataset metadata. Change some units of the variables. Add more table metadata. Add consistence check between metadata and review tables.

@@ -17,14 +17,67 @@
 #
 # LIBRARIES --------------------------------------------------------------------
 #
+library(fs)
 library(tidyverse)
+library(magrittr)
 #
 # OPTIONS ----------------------------------------------------------------------
 #
 #
 # CREATE DATASET METADATA ------------------------------------------------------
 
+review_dataset <-
+  bind_rows(
+    list(
+      name = "documents_registration.csv",
+      description = ""
+    ),
+    list(
+      name = "experiments_characteristics.csv",
+      description = ""
+    ),
+    list(
+      name = "system_management.csv",
+      description = ""
+    ),
+    list(
+      name = "soil_properties.csv",
+      description = ""
+    ),
+    list(
+      name = "tree_component.csv",
+      description = ""
+    ),
+    list(
+      name = "crop_component.csv",
+      description = ""
+    ),
+    list(
+      name = "pasture_component.csv",
+      description = ""
+    ),
+    list(
+      name = "livestock_component.csv",
+      description = ""
+    ),
+    list(
+      name = "emissions.csv",
+      description = ""
+    ),
+    list(
+      name = "radiation.csv",
+      description = ""
+    )
+  )
 
+review_dataset %<>%
+  mutate(
+    number_of_columns = NA_integer_,
+    number_of_rows = NA_integer_,
+    size = NA_real_
+  )
+
+# TODO create metadata to describe the dataset
 
 # CREATE TABLES METADATA -------------------------------------------------------
 
@@ -120,7 +173,7 @@ experiments_characteristics_meta <-
     list(
       name = "total_area",
       description = "The total area of the experiment (all plots together).",
-      unit = "ha (hectar)"
+      unit = "hectar (ha)"
     ),
     list(
       name = "forest_component",
@@ -128,7 +181,7 @@ experiments_characteristics_meta <-
       part of the forestry component (woody species). This variable can
       be composed of one or more species, separated by comma.
       Species identified by scientific name.",
-      unit = "text"
+      unit = "nominal category"
     ),
     list(
       name = "crop_component",
@@ -136,7 +189,7 @@ experiments_characteristics_meta <-
       part of the crop component. This variable can be composed of one
       or more species, separated by comma.
       Species identified by scientific name.",
-      unit = "text"
+      unit = "nominal category"
     ),
     list(
       name = "pasture_component",
@@ -144,7 +197,7 @@ experiments_characteristics_meta <-
       part of the pasture component. This variable can be composed of one
[…]

### 2022-07-25 iclfs_review/lit_review.qmd
Create literature review document using Quarto.

--- 2022-07-07 iclfs_review/lit_review.Rmd
@@
 ---
-title: The aspects of integrated crop-livestock-forest system in Brazil
-
-author: Hugo Tameirão Seixas
-
-output:
-  html_document:
-    theme: readable
-    number_sections: true
-
+title: "Characterization of integrated crop-livestock-forest system in Brazil"
+author: "Hugo Tameirão Seixas"
+format: 
+  html:
+    page-layout: article
+editor: visual
 ---
 
-# Title and Abstract
+## Title and Abstract
 
-# Aims and questions
+## Aims and questions
 
-## Provide a rationale for the review
+### Provide a rationale for the review
 
-## Reference any previous reviews or meta-analyses on the topic
+### Reference any previous reviews or meta-analyses on the topic
 
-## State the aims and scope of the review (including its generality)
+### State the aims and scope of the review (including its generality)
 
@@
 
-## State the primary questions the review addresses (e.g. which moderators were tested)
+### State the primary questions the review addresses (e.g. which moderators were tested)
 
-## Describe whether effect sizes were derived from experimental and/or observational comparisons
+### Describe whether effect sizes were derived from experimental and/or observational comparisons
 
-# Review registration
+## Review registration
 
-# Eligibility criteria
+## Eligibility criteria
 
-# Finding studies
+## Finding studies
 
-## Define the type of search (e.g.comprehensive search, representative sample)
+### Define the type of search (e.g.comprehensive search, representative sample)
 
-## State what sources of information were sought (e.g. published and unpublished studies, personal communications)
+### State what sources of information were sought (e.g. published and unpublished studies, personal communications)
 
-## Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators
+### Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators
 
@@
 
-## Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)
+### Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)
 
-# Study selection
+## Study selection
 
-# Data collection process
+## Data collection process
 
-# Data items
+## Data items
 
-# Assessment of individual study quality
+## Assessment of individual study quality
 
-# Effect size measures
+## Effect size measures
 
-# Missing data
+## Missing data
 
-# Meta-analytic model description
+## Meta-analytic model description
 
-# Software
+## Software
 
-# Non independence
+## Non independence
 
-# Meta-regression and model selection
+## Meta-regression and model selection
 
-# Publication bias and sesitivity analysis
+## Publication bias and sesitivity analysis
 
-# Clarification of post hoc analysis
+## Clarification of post hoc analysis
 
-# Metadata data and code
+## Metadata data and code
 
-# Results of study selection process
+## Results of study selection process
 
-# Sample sizes and study characteristics
+## Sample sizes and study characteristics
 
-# Meta-analysis
+## Meta-analysis
 
-# Heterogeneity
+## Heterogeneity
 
-# Meta-regression
+## Meta-regression
 
-# Outcomes of publication bias and sensitivity analyses
+## Outcomes of publication bias and sensitivity analyses
 
-# Discussion
+## Discussion
 
-# Contributions and funding
+## Contributions and funding
 
-# References
+## References

### 2022-07-26 iclfs_review/review_data_manager.R
Add more metadata.

@@ -787,6 +787,141 @@ crop_component_meta <-
   )
 
 ## Pasture component ----
+crop_component_meta <-
+  bind_rows(
+    list(
+      name = "id",
+      description = "This is a unique identificator for each downloaded
+      document, the first letter indicates the base which the documents
+      was downloaded from (E for embrapa and S for Scopus).",
+      unit = "index"
+    ),
+    list(
+      name = "production_system",
+      description = "Abbreviation of the production system in the experiment:
+      ICLF = Integrated Crop-Livestock-Forestry;
+      ICL = Integrated Crop-Livestock;
+      ILF = Integrated Livestock-Forestry;
+      C = Crop;
+      L = Livestock;
+      F = Forestry;
+      EG = Extensive Grazing;
+      SF = Seasonal Forest.",
+      unit = "nominal category"
+    ),
+    list(
+      name = "plot_id",
+      description = "Unique experiment plot indentificator within the same
+      publication (not unique across publications).",
+      unit = "index"
+    ),
+    list(
+      name = "specie",
+      description = "What is the specie being observed.",
+      unit = ""
+    ),
+    list(
+      name = "spacing",
+      description = "The spacing in relation to the crop component.",
+      unit = "meters (m)"
+    ),
+    list(
+      name = "sowing_rate",
+      description = "The amount of seeds used in one hectare.",
+      unit = "kilograms per hectare (kg/ha)"
+    ),
+    list(
+      name = "position",
+      description = "The position of the observations in relation
+      to the tree component (how far the observations were performed
+      in relation to the trees lines).",
+      unit = "meters"
+    ),
+    list(
+      name = "yield",
+      description = "The total dry matter yield of the pasture.",
+      unit = "kilograms per hectare (kg/ha)"
+    ),
+    list(
+      name = "leaf_yield",
+      description = "The leaf dry matter yield of the pasture.",
+      unit = "kilograms per hectare (kg/ha)"
+    ),
+    list(
+      name = "dry_matter_accumulation",
+      description = "The total dry matter accumulation of the pasture.",
+      unit = "kilograms per hectare per day (kg/ha day)"
+    ),
+    list(
+      name = "digestability",
+      description = "The in vitro digestability of the pasture.",
+      unit = "percentage (%)"
+    ),
+    list(
+      name = "crude_protein",
+      description = "The protein concentration of the pasture.",
+      unit = "percentage (%)"
+    ),
+    list(
+      name = "lai",
+      description = "The leaf area index of the pasture",
[…]

### 2022-07-27 iclfs_review/review_data_manager.R
Add metadata.

@@ -82,7 +82,6 @@ review_dataset %<>%
 # CREATE TABLES METADATA -------------------------------------------------------
 
 ## Documents registration ----
-
 documents_registration_meta <-
   bind_rows(
     list(
@@ -136,7 +135,6 @@ documents_registration_meta <-
   )
 
 ## Experiments characteristics ----
-
 experiments_characteristics_meta <-
   bind_rows(
     list(
@@ -347,7 +345,6 @@ experiments_characteristics_meta <-
 
 
 ## System management ----
-
 system_management_meta <-
   bind_rows(
     list(
@@ -924,9 +921,100 @@ crop_component_meta <-
   )
 
 ## Livestock component ----
+crop_component_meta <-
+  bind_rows(
+    list(
+      name = "id",
+      description = "This is a unique identificator for each downloaded
+      document, the first letter indicates the base which the documents
+      was downloaded from (E for embrapa and S for Scopus).",
+      unit = "index"
+    ),
+    list(
+      name = "production_system",
+      description = "Abbreviation of the production system in the experiment:
+      ICLF = Integrated Crop-Livestock-Forestry;
+      ICL = Integrated Crop-Livestock;
+      ILF = Integrated Livestock-Forestry;
+      C = Crop;
+      L = Livestock;
+      F = Forestry;
+      EG = Extensive Grazing;
+      SF = Seasonal Forest.",
+      unit = "nominal category"
+    ),
+    list(
+      name = "plot_id",
+      description = "Unique experiment plot indentificator within the same
+      publication (not unique across publications).",
+      unit = "index"
+    ),
+    list(
+      name = "specie",
+      description = "What is the specie being observed.",
+      unit = ""
+    ),
+    list(
+      name = "grazing_method",
+      description = "What was the grazing method used in the plot.",
+      unit = ""
+    ),
+    list(
+      name = "live_mean_weigth",
+      description = "The live mean weight of the livestock.",
+      unit = "kilograms (kg)"
+    ),
+    list(
+      name = "average_daily_gain",
+      description = "The weight gain of the livestock per day",
+      unit = "grams per animal per day (g/AU day)"
+    ),
+    list(
+      name = "carcass",
+      description = "The ilograms of carcass produced per hectar.",
+      unit = "kilograms per hectare (kg/ha)"
+    ),
+    list(
+      name = "age",
+      description = "The age of the livestock in months.",
+      unit = "month"
+    ),
+    list(
+      name = "number_of_observations",
[…]

### 2022-07-27 iclfs_review/review_data_manager.R
Add tables description. Create as save metdata as html.

@@ -1,4 +1,4 @@
-# HEADER -----------------------------------------------------------------------
+# HEADER ----------------------------------------------------------------------
 #
 # Title: Review Data Manager
 # Description:
@@ -15,61 +15,106 @@
 #
 #
 #
-# LIBRARIES --------------------------------------------------------------------
+# LIBRARIES -------------------------------------------------------------------
 #
 library(fs)
-library(tidyverse)
 library(magrittr)
+library(gt)
+library(glue)
+library(tidyverse)
 #
-# OPTIONS ----------------------------------------------------------------------
+# OPTIONS ---------------------------------------------------------------------
 #
 #
-# CREATE DATASET METADATA ------------------------------------------------------
+# CREATE DATASET METADATA -----------------------------------------------------
 
+# Create a table describing the files that composes the dataset
 review_dataset <-
   bind_rows(
     list(
-      name = "documents_registration.csv",
-      description = ""
+      name = "01_documents_registration.csv",
+      description = "This table stores general information about the document.
+      There are no data from experiments stored here. This table will provide
+      information to identify the documents, its authors, year of publication.
+      Will also store observations and quotes from the documents."
     ),
     list(
-      name = "experiments_characteristics.csv",
-      description = ""
+      name = "02_experiments_characteristics.csv",
+      description = "This table is composed of specific information of the
+      experiment as a whole. What are the farming systems analysed,
+      the location, what are the species and some more information. It is
+      linked to the {documents_registration} table by the unique identifier
+      of the document."
     ),
     list(
-      name = "system_management.csv",
-      description = ""
+      name = "03_system_management.csv",
+      description = "Stores data about how is the management of each
+      experimental plot of the experiment. You can find data regarding
+      fertilization and supplementary diet in this table. It is linked to the
+      {experiments_characteristics} table by the unique identifiers of
+      the document and the experimental plot."
     ),
     list(
-      name = "soil_properties.csv",
-      description = ""
+      name = "04_soil_properties.csv",
+      description = "Stores data about properties of the soil in the
+      experimental plot, along the soil profile and position.
+      Examples of stored variables are the bulk density, soil texture,
[…]

### 2022-07-27 iclfs_review/review_data_manager.R
Check consistence of all tables. Create table of all variables.

@@ -1243,71 +1243,129 @@ headers_list <-
         mutate(publication_year = as.integer())
 
     }
-  )
+  ) %>%
+  purrr::set_names(review_dataset$name)
 
 # CHECK CONSISTENCE -----------------------------------------------------------
 
-# Check if review table already exists
-if (file_exists("iclfs_review/tables/documents_registration.csv")) {
+walk2(
+  .x = headers_list,
+  .y = names(headers_list),
+  function(header_table, file) {
 
-  documents_registration <- read_delim(
-    "iclfs_review/tables/documents_registration.csv",
-    delim = ";",
-    col_types = list(col_character())
-  )
+    # Check if review table already exists
+    if (file_exists(glue("iclfs_review/tables/{file}"))) {
 
-} else { # If table does not exists, create one from the metadata
+      table <- read_delim(
+        glue("iclfs_review/tables/{file}"),
+        delim = ";",
+        col_types = list(col_character())
+      )
 
-  write_delim(
-    documents_registration_header,
-    "iclfs_review/tables/documents_registration.csv",
-    delim = ";"
-  )
+    } else { # If table does not exists, create one from the metadata
 
-  documents_registration <- read_delim(
-    "iclfs_review/tables/documents_registration.csv",
-    delim = ";",
-    col_types = list(col_character())
-  )
+      write_delim(
+        header_table,
+        glue("iclfs_review/tables/{file}"),
+        delim = ";"
+      )
 
-}
+      table <- read_delim(
+        glue("iclfs_review/tables/{file}"),
+        delim = ";",
+        col_types = list(col_character())
+      )
 
-# Check if all columns in the review table are in the metadata
-col_check <-
-  all(
-    names(documents_registration) %in% names(documents_registration_header)
-  )
+    }
 
-if (col_check & nrow(documents_registration) > 0) {
+    # Check if all columns in the review table are in the metadata
+    col_check <-
+      all(
+        names(table) %in% names(header_table)
+      )
 
-  # If review table is consistent with metadata, merge them
-  bind_rows(documents_registration_header, documents_registration)
+    if (col_check & nrow(table) > 0) {
 
-} else if (nrow(documents_registration) == 0) {
+      # If review table is consistent with metadata, merge and save them
 
-  stop(
[…]

### 2022-07-27 iclfs_review/lit_review.qmd
Update search strings.

@@
 
-Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril)
+Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril) AND PUBYEAR > 1999
 
-Embrapa: (ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)
+Embrapa: ((ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)) AND (ano-publicacao:[2000 TO *]) AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP" OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT") AND (idioma:"Inglês" OR idioma:"Português")
 

### 2022-07-27 iclfs_review/review_data_manager.R
Add search strings metadata.

@@ -26,6 +26,58 @@ library(tidyverse)
 # OPTIONS ---------------------------------------------------------------------
 #
 #
+# CREATE LITERATURE SEARCH METADATA -------------------------------------------
+
+bind_rows(
+  list(
+    database = "Scopus",
+    database_url = "https://www.scopus.com/",
+    search_string = glue(
+      "TITLE-ABS-KEY(",
+      "iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest",
+      "OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR",
+      "agrosilvipastoril) AND PUBYEAR > 1999"
+    ),
+    oldest_publication_date = 2007,
+    newest_publication_date = 2022
+  ),
+  list(
+    database = "Embrapa",
+    database_url = "https://www.bdpa.cnptia.embrapa.br/consulta/busca",
+    search_string = glue(
+      '((ICLF) OR (iclfs) OR (crop-livestock-forestry)',
+      'OR (crop-livestock-forest) OR (agrosilvipastoral)',
+      'OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril))',
+      'AND (ano-publicacao:[2000 TO *])',
+      'AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP"',
+      'OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT")',
+      'AND (idioma:"Inglês" OR idioma:"Português")'),
+    oldest_publication_date = 2000,
+    newest_publication_date = 2022
+  )
+) %>%
+  rename_with( ~ str_replace_all(., "_", " ")) %>%
+  gt() %>%
+  tab_header(title = "LITERATURE SEARCH") %>%
+  tab_options(
+    heading.background.color = "#d2d2d2",
+    table.border.top.width = 3,
+    table.border.top.color = "#666663",
+    heading.border.bottom.width = 3,
+    heading.border.bottom.color = "#666663",
+    table.border.bottom.width = 3,
+    table.border.bottom.color = "#666663"
+  ) %>%
+  tab_source_note(
+    "The search strategy was to include a wide variety of terms that are
+    commonly used to refer an integrated crop-livestock-forestry system (ICLFS).
+    This makes the search very broad, which gives us everything that have
+    been researched about ICLFS. The inclusion of the Embrapa database is
+    utmost important to create an overview of this system in Brazil, since it
[…]

### 2022-07-28 iclfs_review/review_data_manager.R
Fix search strings metadata.

@@ -32,7 +32,7 @@ bind_rows(
   list(
     database = "Scopus",
     database_url = "https://www.scopus.com/",
-    search_string = glue(
+    search_string = glue(.sep = " ",
       "TITLE-ABS-KEY(",
       "iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest",
       "OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR",
@@ -44,14 +44,15 @@ bind_rows(
   list(
     database = "Embrapa",
     database_url = "https://www.bdpa.cnptia.embrapa.br/consulta/busca",
-    search_string = glue(
+    search_string = glue(.sep = " ",
       '((ICLF) OR (iclfs) OR (crop-livestock-forestry)',
       'OR (crop-livestock-forest) OR (agrosilvipastoral)',
       'OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril))',
       'AND (ano-publicacao:[2000 TO *])',
       'AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP"',
       'OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT")',
-      'AND (idioma:"Inglês" OR idioma:"Português")'),
+      'AND (idioma:"Inglês" OR idioma:"Português")'
+    ),
     oldest_publication_date = 2000,
     newest_publication_date = 2022
   )

### 2022-07-28 manuscript/manuscript.qmd
Create manuscript and references files.

---
title: Integrated farming and global warming mitigation in Brazil
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
toc: true
toc-title: Contents
format: 
  html:
    theme: lux
page-layout: article
editor: visual
bibliography: references.bib
link-citations: true
abstract: "One of the targets in Brazil’s Nationally Determined Contribution (NDC) to the Paris Agreement is the expansion of 5 million hectares of integrated crop-livestock-forestry systems (ICLFS) until 2030. Although there is some notion of the extent where this expansion could occur, there is no systematic accounting on the role of soil carbon to bring this agricultural system to carbon neutrality, or even to be a sink of carbon. In that context, the objective of this research plan is to produce spatially-explicit projections of the expansion of ICLFS predicted in Brazil’s NDC and estimate the carbon balance, the provision of other ecosystem services and financial revenue. This will be done with the use of empirical models built upon published data. The final results of this study will provide information for decision makers, for the implementation of ICLFS across Brazil."
---

```{r}
#| include: false
  library(nomnoml)
```

---

# Introduction

ICLF are nice [@FREITAS2020]

It is well known that AFOLU (Agriculture, Forestry and Land Use) and BECCS (Bioenergy with Carbon Capture and Storage) sectors are key to slow down the increase of CO 2 concentration in the atmosphere, by reducing emissions and also
fixing carbon (IPCC 2018). As part of the Paris Agreement, Brazil pledged to stop illegal deforestation and to reforest 12 million of hectares by 2030 to help mitigating global warming, in addition, it also committed to restore 15 million hectares of pasturelands and expand the area of ICLFS to 5 million hectares.

---

# Objectives

1. What are the management practices that lead to the best com- promise between carbon sequestration and financial revenue for agricultural land under ICLFS?

2. Can indirect land-use and land-cover changes, especially land sparing under expansion of ICLFS, improve the net carbon budget of this agricultural system?

3. Does the prioritization of the provision of ecosystem services other than carbon storage imply in changes of productivity of ICLFS?

4. Can further expansion of ICLFS, beyond Brazil’s NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?

---

# Materials and Methods

In order to achieve the proposed objective, the work will be divided in four major
parts:

1. ICLFS management scenario elaboration;

2. Adaptation and application of the modeling framework to ICLFS;

3. Estimate the carbon balance, ecosystem services, and economic evaluation
based on outputs from modeling framework;

4. Results consolidation and analysis;

```{nomnoml}
#| echo: false

# direction: down
# .box: dashed
[Start]-[Finish!]
[Finish!]-[<box>blablablablabla
           lablablablablablabla]

```

### Integrated crop-livestock-forest overview

#### Literature review

#### Experts survey

### Model projections

---

# Results

---

# Discussion

---

# Conclusions

---

# Supporting Information

# References

### 2022-07-29 manuscript/manuscript.qmd
Change methods diagram.

@@
 #| include: false
-  library(nomnoml)
+
+library(DiagrammeR)
 ```
 
----
+------------------------------------------------------------------------
 
@@
 
-It is well known that AFOLU (Agriculture, Forestry and Land Use) and BECCS (Bioenergy with Carbon Capture and Storage) sectors are key to slow down the increase of CO 2 concentration in the atmosphere, by reducing emissions and also
-fixing carbon (IPCC 2018).
+It is well known that AFOLU (Agriculture, Forestry and Land Use) and BECCS (Bioenergy with Carbon Capture and Storage) sectors are key to slow down the increase of CO 2 concentration in the atmosphere, by reducing emissions and also fixing carbon (IPCC 2018).
 As part of the Paris Agreement, Brazil pledged to stop illegal deforestation and to reforest 12 million of hectares by 2030 to help mitigating global warming, in addition, it also committed to restore 15 million hectares of pasturelands and expand the area of ICLFS to 5 million hectares.
 
----
+------------------------------------------------------------------------
 
@@
 4.
-Can further expansion of ICLFS, beyond Brazil’s NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?
+Can further expansion of ICLFS, beyond Brazil's NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?
 
----
+------------------------------------------------------------------------
 
@@
 
-In order to achieve the proposed objective, the work will be divided in four major
-parts:
+In order to achieve the proposed objective, the work will be divided in four major parts:
 
@@
 
-3. Estimate the carbon balance, ecosystem services, and economic evaluation
-based on outputs from modeling framework;
+3.  Estimate the carbon balance, ecosystem services, and economic evaluation based on outputs from modeling framework;
 
@@
 
-```{nomnoml}
+```{r}
 #| echo: false
 
-# direction: down
-# .box: dashed
-[Start]-[Finish!]
-[Finish!]-[<box>blablablablabla
-           lablablablablablabla]
+grViz(
+  "digraph {
+
+  graph [layout = dot, rankdir = TD, nodesep = 1.2, ranksep = 0.12]
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.2,
+        fontsize = 11]
+
+  a [label = 'Literature \n Review']
+  b [label = 'Experts \n Survey']
+  c [label = 'ICLF \n Database']
+  d [label = 'Modelling \n Scenarios']
+  e [label = 'ICLF \n Expantion \n Projections']
+  f [label = 'Services \n Estimations']
+
+  a -> {b c} b -> c
+  c -> {d e f} d -> e 
+  e -> f
+
+  }"
+)
 
@@
 
-### Model projections
+#### Integrated crop-livestock-forest database
 
----
+### Model framework
+
+#### Modelling scenarios
+
+#### Integrated crop-livestock-forest expansion projections
+
+#### Services estimations
+
+------------------------------------------------------------------------
 
@@
 
----
+------------------------------------------------------------------------
 

### 2022-07-29 manuscript/manuscript.qmd
Add info to methods diagram and add one section to methods.

@@
 
-  graph [layout = dot, rankdir = TD, nodesep = 1.2, ranksep = 0.12]
+  graph [layout = dot, rankdir = TD, nodesep = 1, ranksep = 0.13]
 
@@
 
+  g [label = 'Directed \n literature \n analysis']
+  h [label = 'Critical \n reflection']
+
   a -> {b c} b -> c
@@
   e -> f
+
+  g -> h
+  f -> h
 
@@
 
+### Reflection about the role of integrated crop-livestock-forest systems in the agrarian question
+
+ICLF and the agrarian question, a directed reading towards the construction of a narrative reflection.
+Environmental (e.g.
+climate change and biodiversity) and social (e.g.
+social inequality, food insecurity) contexts.
+
 ------------------------------------------------------------------------

### 2022-08-01 manuscript/manuscript.qmd
Rewrite abstract. Start rewriting introduction.

--- 2022-07-28 manuscript/manuscript.qmd
@@
 link-citations: true
-abstract: "One of the targets in Brazil’s Nationally Determined Contribution (NDC) to the Paris Agreement is the expansion of 5 million hectares of integrated crop-livestock-forestry systems (ICLFS) until 2030.
-Although there is some notion of the extent where this expansion could occur, there is no systematic accounting on the role of soil carbon to bring this agricultural system to carbon neutrality, or even to be a sink of carbon.
-In that context, the objective of this research plan is to produce spatially-explicit projections of the expansion of ICLFS predicted in Brazil’s NDC and estimate the carbon balance, the provision of other ecosystem services and financial revenue.
-This will be done with the use of empirical models built upon published data.
-The final results of this study will provide information for decision makers, for the implementation of ICLFS across Brazil."
+abstract: "There is a high expectation in the reduction of liquid greenhouse gases in Brazil by the implementation of integrated crop-livestock-forestry systems.
+The foundation of such expectation relies in the hyphothesis that these systems are capable of storing more above and below ground carbon, in relation to conventional farming systems, due to the presence of trees.
+However, that are not robust estimates about the pottential of these systems to store carbon in a national scale, and usually point estimates are used to extrapolate carbon sequestration.
+In order to improve the representation of carbon sequestration by integrated crop-livestock-forestry systems, this project aims to use published data to develop a spatially explicit model to estimate carbon fluxes in Brazil."
 ---
@@
 
-ICLF are nice [@FREITAS2020]
+The implementation of integrated crop-livestock-forestry (ICLF) systems in Brazil are expected to sequester enough carbon to contribute to reduce annual liquid carbon emissions.
+Despite the expectations, there are not clear estimates of the magnitude of reductions of liquid emissions caused by ICLF expansion.
+Field studies show contrasting results.
+@Valani2022 observed a higher organic carbon content in the soil in relation to conventional grazing and other integrated systems.
+@Bieluczyk2020 field measurements did not show clear differences between extensive grazing and ICLF soil organic matter, with highly temporal heterogeneity in observations.
+@Silva2018837 found inconsistent differences of soil total organic carbon between pasture and ILPF system due to high heterogeneity of observations along the soil layers, and observed small differences between agriculture and integrated system, in which the agriculture presented higher carbon stocks.
+@Oliveira2018105 found higher amounts of soil organic carbon of two ICLF systems and continuous pasture areas, there were also observed differences between the two integrated systems.
 
-It is well known that AFOLU (Agriculture, Forestry and Land Use) and BECCS (Bioenergy with Carbon Capture and Storage) sectors are key to slow down the increase of CO 2 concentration in the atmosphere, by reducing emissions and also
-fixing carbon (IPCC 2018).
-As part of the Paris Agreement, Brazil pledged to stop illegal deforestation and to reforest 12 million of hectares by 2030 to help mitigating global warming, in addition, it also committed to restore 15 million hectares of pasturelands and expand the area of ICLFS to 5 million hectares.
-
----
+------------------------------------------------------------------------
 

### 2022-08-02 manuscript/manuscript.qmd
Write second paragraph of introduction.

@@
 @Oliveira2018105 found higher amounts of soil organic carbon of two ICLF systems and continuous pasture areas, there were also observed differences between the two integrated systems.
+
+Unfortunately, estimates of carbon sequestration by ICLF at larger scales usually use point estimates, which can severely bias the results towards one direction.
+@Azevedo_2018 used a CO<sub>2</sub>-eq removal factor of -6.24 t CO<sub>2</sub>-eq ha<sup>-1</sup> y<sup>-1</sup>, which was extracted from one experiment comparing integrated crop-livestock (ICL) systems to pasture [@Carvalho_2010], and did not observe consistent differences between these types of systems.
+The removal factor was then extrapolated over estimated ILPF area, this simplification is the best guess that Brazil have over the potential of integrated systems in reducing liquid emissions.
+In face of such scenario, this study aims to generate estimations of CO<sub>2</sub>-eq removal accounting for variation in many aspects, soil attributes, ICLF system characteristics, species used, spacing and climate.
+We expect that such estimations will provide more realistic ranges of possible outcomes in a diverse set of future scenarios of ICLF expansion in Brazil.
 

### 2022-08-02 iclfs_review/lit_review.qmd
Change document style. Add more information about the review.

@@
     page-layout: article
-editor: visual
+    toc: true
+    toc-depth: 2
+number-sections: true
 ---
@@
 ## Title and Abstract
+
+### Identify the review as a systematic review, meta-analysis, or both
+
+This is a systematic review
+
+### Summarise the aims and scope of the review
+
+The main objective of this review is to synthesize data concerning ICLF in different aspects, creating an overview of the main characteristics of the ICLF being researched in Brazil.
+I will analyse variables such as above and below ground productivity of the tree, pasture and crop components; livestock productivity; system management characteristics; soil attributes; GHG emissions.
+I will evaluate national and international research conducted inside the Brazilian territory.
+
+### Describe the data set
+
+The data set will be composed by a collection of relational tables, each table will describe a characteristic of the ICLF in Brazil.
+
+### State the results of the primary outcome
+
+### State conclusions
+
+### State limitations
 
@@
 
+The review will be performed over any research that analysed any aspect of the ICLF in Brazil.
+Therefore this is a very general approach, which is feasible due to the limited amount of research in this topic.
+Only documents which are not explicitly about ICLF will be removed from the review.
+
+I will extract data of a diverse number of variables, which will allow me to create an overview of the characteristics of the ICLF systems being analysed in Brazil.
+
 ### Reference any previous reviews or meta-analyses on the topic
+
+I have not yet identified any systematic review about ICLF in Brazil.
 

### 2022-08-02 manuscript/manuscript.qmd
Fix typos.

@@
 abstract: "There is a high expectation in the reduction of liquid greenhouse gases in Brazil by the implementation of integrated crop-livestock-forestry systems.
-The foundation of such expectation relies in the hyphothesis that these systems are capable of storing more above and below ground carbon, in relation to conventional farming systems, due to the presence of trees.
-However, that are not robust estimates about the pottential of these systems to store carbon in a national scale, and usually point estimates are used to extrapolate carbon sequestration.
+The foundation of such expectation relies in the hypothesis that these systems are capable of storing more above and below ground carbon, in relation to conventional farming systems, due to the presence of trees.
+However, that are not robust estimates about the potential of these systems to store carbon in a national scale, and usually point estimates are used to extrapolate carbon sequestration.
 In order to improve the representation of carbon sequestration by integrated crop-livestock-forestry systems, this project aims to use published data to develop a spatially explicit model to estimate carbon fluxes in Brazil."

### 2022-08-03 manuscript/manuscript.qmd
Update objectives. Add diagrams in the matherials section.

@@
 page-layout: article
-editor: visual
 bibliography: references.bib
@@
 #| include: false
-  library(nomnoml)
+
+library(DiagrammeR)
 ```
@@
 
-1.  What are the management practices that lead to the best com- promise between carbon sequestration and financial revenue for agricultural land under ICLFS?
+The present work is composed by three main objectives, accompanied by parallel related questions:
 
-2.  Can indirect land-use and land-cover changes, especially land sparing under expansion of ICLFS, improve the net carbon budget of this agricultural system?
+1. Develop an overview about the ICLF experiments characteristics being conducted in Brazil;
 
-3.  Does the prioritization of the provision of ecosystem services other than carbon storage imply in changes of productivity of ICLFS?
+    1.1. What is the productivity of each component of ICLF systems of different characteristics?
 
-4.
-Can further expansion of ICLFS, beyond Brazil's NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?
+    1.2. What are the effects of ICLF systems over soils characteristcs?
+
+    1.3. What are the management characteristics of ICLF systems?
+
+    1.4. WHat is the economical revenue of ICLF systems?
+
+    1.5. What is the pottential expansion of ICLF systems in Brazil?
+
+2. Estimate the potential of ICLF systems to remove carbon from the atmosphere by 2030 and 2050;
+
+    2.1. What are the ICLF system management characteristics that provide the best balance between carbon removal, productivity and financial revenue?
+
+    2.2. What are the main factors that influence the carbon removal in the modelling framework?
+
+    2.3. What is the pottential of the expansion of ICLF systems in the emissions reduction pledges made by Brazil?
+
+3.  Evaluate the feasibility of the implementation of ICLF as a mean to reduce emissions, in relation to different perspectives of solutions to avoid climatic catastrophe;
+
+    3.1. Does the expansionof ICLF systems taking into account equity and possible social impacts, as a public policy?
+
+    3.2. The actual strategies to promote the adoption of ICLF systems are being effective?
 
@@
 
-In order to achieve the proposed objective, the work will be divided in four major parts:
+In order to achieve the proposed objective, the work will be divided in three major parts:
 
-1.  ICLFS management scenario elaboration;
+1. Overview of ICLF characteristics in Brazil;
 
-2.  Adaptation and application of the modeling framework to ICLFS;
+2. Future projections and estimates of benefits generated by ICLF systems adoption;
 
-3.  Estimate the carbon balance, ecosystem services, and economic evaluation based on outputs from modeling framework;
+3. Critical analysis of ICLF as a public policy to curb climate change;
 
-4.  Results consolidation and analysis;
-
-```{nomnoml}
+```{r}
 #| echo: false
 
-# direction: down
-# .box: dashed
-[Start]-[Finish!]
-[Finish!]-[<box>blablablablabla
-           lablablablablablabla]
+grViz(
+  "digraph {
+
+  graph [layout = dot, rankdir = TD, nodesep = 0.9, ranksep = 0.3]
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.5,
+        fontsize = 12]
+
+  edge [penwidth = 1.5]
+
+  a [label = 'Systematic \n Review', xlabel = '1']
+  b [label = 'Experts Survey', xlabel = '1']
+  c [label = 'ICLF overview \n data set', xlabel = '1']
+  d [label = 'Projections \n Scenarios', xlabel = '2']
+  e [label = 'LULC \n Projections', xlabel = '2']
+  f [label = 'Benefits \n Estimations', xlabel = '2']
+  g [label = 'Targeted \n Review', xlabel = '3']
+  h [label = 'Narrative \n Discussion', xlabel = '3']
+
+  a -> c b -> c
+  c -> d d -> e
+  e -> f c -> f
+  f -> h g -> h
+
+  }"
+)
 
@@
 ### Model projections
+
+```{r}
+#| include: false
+
+grViz(
+  "digraph {
+
+  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
+
+  edge [penwidth = 1.5]
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.9,
+        fontsize = 12]
+
+  a [label = 'Degraded \n Pastures']
+  b [label = 'Temperature']
+  c [label = 'Precipitation']
+  d [label = 'Potential \n Evapotranspiration']
+  e [label = 'Soil Texture']
+  f [label = 'System \n Management']
+  g [label = 'LULC/Management \n Time Series']
+  h [label = 'Productivity']
+  i [label = 'Litter']
+  j [label = 'Decomposition Rates']
+  k [label = 'Below Ground Carbon']
+  l [label = 'Above Ground Carbon']
+  m [label = 'Emissions']
+  n [label = 'Carbon Balance']
+
+    node [shape = ellipse,
+        fontname = Helvetica,
+        style = dashed,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.5,
+        fontsize = 12]
+
+  1 [label = 'LULC Model']
+  2 [label = 'Soil Carbon Model']
+  3 [label = 'Productivity Model']
+  4 [label = 'Economic Model']
+
+  a -> 1 f -> 1 1 -> g
+  g -> 2 b -> 2 c -> 2 d -> 2 e -> 2 i -> 2 j -> 2 2 -> k h -> 2
+  g -> 3 b -> 3 c -> 3 e -> 3 3-> h 3 -> i h -> i 2 -> l i -> l h -> m
+  h -> 4
+  k -> n l -> n m -> n
+
+  }"
+)
+
+```
+
+#### Projections scenarios
+
+#### LULC projections
+
+```{r}
+#| echo: false
+
+grViz(
+  "digraph {
+
+  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
+
+  edge [penwidth = 1.5]
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.9,
+        fontsize = 12]
+
+  a [label = 'Degraded \n Pastures']
+  b [label = 'System \n Management']
+  c [label = 'LULC Scenarios']
+  d [label = 'LULC/Management \n Time Series']
+
+    node [shape = ellipse,
+        fontname = Helvetica,
+        style = dashed,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.5,
+        fontsize = 12]
+
+  1 [label = 'LULC Model']
+
+  a -> 1 b -> 1 c -> 1 1 -> d
+
+  }"
+)
+
+```
+
+#### Benefits estimations
+
+```{r}
+#| echo: false
+
+grViz(
+  "digraph {
+
+  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
+
+  edge [penwidth = 1.5]
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.9,
+        fontsize = 12]
+
+  a [label = 'LULC/Management \n Time Series']
+  b [label = 'Temperature']
+  c [label = 'Precipitation']
+  d [label = 'Potential \n Evapotranspiration']
+  e [label = 'Soil Texture']
+  h [label = 'Productivity']
+  i [label = 'Litter']
+  j [label = 'Decomposition Rates']
+
+  node [shape = ellipse,
+        fontname = Helvetica,
+        style = dashed,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 1.5,
+        width = 1.5,
+        fontsize = 12]
+
+  1 [label = 'Productivity Model']
+  2 [label = 'Soil Carbon Model']
+  3 [label = 'Economic Model']
+
+  a -> 1 a -> 2 a -> 3
+
+  b -> 1 c -> 1 d -> 1 e -> 1
+  1 -> h 1 -> i
+
+  b -> 2 c -> 2 d -> 2 e -> 2 j -> 2 i -> 2
+
+  h -> 3
+
+  }"
+)
+
+```
+
+### Critical analysis
 

### 2022-08-08 manuscript/manuscript.qmd
Add appendix with license.

@@
 In order to improve the representation of carbon sequestration by integrated crop-livestock-forestry systems, this project aims to use published data to develop a spatially explicit model to estimate carbon fluxes in Brazil."
+appendix-style: plain
+license: CC BY-NC-ND 4.0
 ---

### 2022-08-12 manuscript/manuscript.qmd
Fix typo.
Improve objectives section.

@@
 library(DiagrammeR)
+
 ```
@@
 
-1. Develop an overview about the ICLF experiments characteristics being conducted in Brazil;
+1. Identify ICLF systems characteristics and dynamics in Brazil;
 
-    1.1. What is the productivity of each component of ICLF systems of different characteristics?
+    1.1. What are the management characteristics of ICLF systems?
 
-    1.2. What are the effects of ICLF systems over soils characteristcs?
+    1.2. What are the compositions of each component of ICLF systems?
 
-    1.3. What are the management characteristics of ICLF systems?
+    1.3. What is the productivity of each component of ICLF systems?
 
-    1.4. WHat is the economical revenue of ICLF systems?
+    1.4 What are the effects of ICLF system over soil properties?
 
-    1.5. What is the pottential expansion of ICLF systems in Brazil?
+    1.5. What is the economical revenue of ICLF systems?
 
-2. Estimate the potential of ICLF systems to remove carbon from the atmosphere by 2030 and 2050;
+    1.6. What is the potential expansion of ICLF systems in Brazil?
+
+2. Estimate the potential of ICLF systems to provide benefits, in the context of climate change;
 
@@
 
-    2.3. What is the pottential of the expansion of ICLF systems in the emissions reduction pledges made by Brazil?
+    2.3. What is the pottential of the expansion of ICLF systems over the emissions reduction pledges made by Brazil?
 
-3.  Evaluate the feasibility of the implementation of ICLF as a mean to reduce emissions, in relation to different perspectives of solutions to avoid climatic catastrophe;
+3.  Evaluate the implementation of ICLF as a mean to curb and mitigate climate change, in relation to different perspectives of solutions to avoid climatic catastrophe;
 
-    3.1. Does the expansionof ICLF systems taking into account equity and possible social impacts, as a public policy?
+    3.1. Does the expansion of ICLF systems taking into account equity and possible social impacts, as a public policy?
 

### 2022-09-20 manuscript/manuscript.qmd
Add schedule, improve diagrams, add text.

@@
 library(DiagrammeR)
+library(lubridate)
+library(tidyverse)
 
@@
 
-    1.4 What are the effects of ICLF system over soil properties?
+    1.4. What are the effects of ICLF system over soil properties?
 
@@
 
+    3.3. Does focusing on lowering net emissions a distraction from lowering gross emissions?
+
 ------------------------------------------------------------------------
@@
 
-  graph [layout = dot, rankdir = TD, nodesep = 0.9, ranksep = 0.3]
+  graph [layout = dot, 
+         rankdir = TD, 
+         nodesep = 2, 
+         ranksep = 0.5,
+         tooltip = ' ']
 
@@
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.5,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  edge [penwidth = 1.5]
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
 
@@
 
+#### Projections scenarios
+
 ```{r}
-#| include: false
+#| echo: false
 
@@
 
-  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
-
-  edge [penwidth = 1.5]
+  graph [layout = dot,
+         rankdir = TD, 
+         nodesep = 2, 
+         ranksep = 0.4,
+         tooltip = ' ']
 
@@
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.9,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  a [label = 'Degraded \n Pastures']
-  b [label = 'Temperature']
-  c [label = 'Precipitation']
-  d [label = 'Potential \n Evapotranspiration']
-  e [label = 'Soil Texture']
-  f [label = 'System \n Management']
-  g [label = 'LULC/Management \n Time Series']
-  h [label = 'Productivity']
-  i [label = 'Litter']
-  j [label = 'Decomposition Rates']
-  k [label = 'Below Ground Carbon']
-  l [label = 'Above Ground Carbon']
-  m [label = 'Emissions']
-  n [label = 'Carbon Balance']
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
 
-    node [shape = ellipse,
-        fontname = Helvetica,
-        style = dashed,
-        fontcolor = '#343a40'
-        fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.5,
-        fontsize = 12]
+  a [label = 'Region']
+  b [label = 'Species']
+  c [label = 'Population']
+  d [label = 'Cycle Length']
+  e [label = 'Management \n Practices']
 
-  1 [label = 'LULC Model']
-  2 [label = 'Soil Carbon Model']
-  3 [label = 'Productivity Model']
-  4 [label = 'Economic Model']
-
-  a -> 1 f -> 1 1 -> g
-  g -> 2 b -> 2 c -> 2 d -> 2 e -> 2 i -> 2 j -> 2 2 -> k h -> 2
-  g -> 3 b -> 3 c -> 3 e -> 3 3-> h 3 -> i h -> i 2 -> l i -> l h -> m
-  h -> 4
-  k -> n l -> n m -> n
+  a -> b b -> c
+  b -> d b -> e
 
@@
 ```
-
-#### Projections scenarios
 
@@
 
-  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
-
-  edge [penwidth = 1.5]
+  graph [layout = dot,
+         rankdir = LR, 
+         nodesep = 1.2, 
+         ranksep = 0.5,
+         tooltip = ' ']
 
@@
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.9,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  a [label = 'Degraded \n Pastures']
-  b [label = 'System \n Management']
-  c [label = 'LULC Scenarios']
-  d [label = 'LULC/Management \n Time Series']
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
 
-    node [shape = ellipse,
+  a [label = 'Pasture']
+  b [label = 'Transition \n (ICL)']
+  c [label = 'ICLF']
+
+    node [shape = oval,
         fontname = Helvetica,
-        style = dashed,
+        style = filled,
         fontcolor = '#343a40'
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.5,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  1 [label = 'LULC Model']
+  e [label = 'Random Variables']
+  f [label = 'Expansion \n Scenario']
 
-  a -> 1 b -> 1 c -> 1 1 -> d
+      node [shape = diamond,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
+
+  d [label = 'Random \n Selection']
+
+  a -> d b -> c c -> b 
+  d -> b e -> b e -> c
+  f -> d
 
@@
 
-grViz(
+grViz(height = 500,
   "digraph {
 
-  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]
-
-  edge [penwidth = 1.5]
+  graph [layout = dot,
+         rankdir = TD, 
+         nodesep = 1.2, 
+         ranksep = 0.5,
+         tooltip = ' ']
 
@@
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.9,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  a [label = 'LULC/Management \n Time Series']
-  b [label = 'Temperature']
-  c [label = 'Precipitation']
-  d [label = 'Potential \n Evapotranspiration']
-  e [label = 'Soil Texture']
-  h [label = 'Productivity']
-  i [label = 'Litter']
-  j [label = 'Decomposition Rates']
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
 
-  node [shape = ellipse,
+  a [label = 'Biomass']
+  b [label = 'Soil Carbon \n (Century)']
+  c [label = 'Productivity']
+  d [label = 'Revenue']
+
+    node [shape = oval,
         fontname = Helvetica,
-        style = dashed,
+        style = filled,
         fontcolor = '#343a40'
         fillcolor = '#f7f7f9'
-        penwidth = 1.5,
-        width = 1.5,
-        fontsize = 12]
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
 
-  1 [label = 'Productivity Model']
-  2 [label = 'Soil Carbon Model']
-  3 [label = 'Economic Model']
+  e [label = 'Population']      
+  f [label = 'Climate']
+  g [label = 'Species']
+  h [label = 'Management \n Practices']
 
-  a -> 1 a -> 2 a -> 3
+  a -> b a -> c c -> d
 
-  b -> 1 c -> 1 d -> 1 e -> 1
-  1 -> h 1 -> i
-
-  b -> 2 c -> 2 d -> 2 e -> 2 j -> 2 i -> 2
-
-  h -> 3
+  e -> a e -> c
+  f -> a f -> b f -> c
+  g -> a g ->b g -> c
+  h -> d
 
@@
 
+# Schedule
+
+```{r}
+#| echo: false
+
+schedule_table <- 
+  bind_rows(
+    list(
+      activity = "Systematic Review",
+      start = "01-10-2022",
+      end = "01-06-2023",
+      section = 1
+    ),
+    list(
+      activity = "Experts Survey Development",
+      start = "01-10-2022",
+      end = "01-04-2023",
+      section = 1
+    ),
+    list(
+      activity = "Experts Survey Application",
+      start = "01-04-2023",
+      end = "01-08-2023",
+      section = 1
+    ),
+    list(
+      activity = "Model Prototype Development",
+      start = "01-10-2022",
+      end = "01-09-2023",
+      section = 2
+    ),
+    list(
+      activity = "Projection Scenarios Development",
+      start = "01-07-2023",
+      end = "01-09-2023",
+      section = 2
+    ),
+    list(
+      activity = "LULC Projections",
+      start = "01-09-2023",
+      end = "01-11-2023",
+      section = 2
+    ),
+    list(
+      activity = "Benefits Estimations",
+      start = "01-11-2023",
+      end = "01-04-2024",
+      section = 2
+    ),
+    list(
+      activity = "Targeted Review",
+      start = "01-01-2024",
+      end = "01-06-2024",
+      section = 3
+    ),
+    list(
+      activity = "Narrative Discussion",
+      start = "01-04-2024",
+      end = "01-08-2024",
+      section = 3
+    ),
+    list(
+      activity = "Final Manuscript Development",
+      start = "01-08-2024",
+      end = "01-02-2025",
+      section = NA
+    )
+  )
+
+schedule_table <- schedule_table %>%
+  mutate(
+    start = dmy(start),end = dmy(end),
+    activity = factor(activity, levels = activity)
+  ) %>%
+  pivot_longer(
+    cols = c(start, end),
+    names_to = "when",
+    values_to = "date"
+  )
+
+schedule_table %>%
+    ggplot() +
+    geom_line(
+      aes(x = date, y = activity), 
+      size = 3, 
+      lineend = "round"
+    ) +
+    scale_y_discrete(limits = rev) +
+    scale_x_date(
+      date_labels = "%b-%Y", 
+      date_breaks = "6 months", 
+      date_minor_breaks = "1 month",
+      limits = c(ymd("2022-09-01"), ymd("2025-03-01"))
+    ) +
+    labs(color = "Section") +
+    theme_minimal() + 
+    theme(
+      text = element_text(family = "sans", size = 15),
+      panel.grid.major = element_line(color = "#a9a9a9"),
+      axis.title = element_blank(),
+      axis.text.x = element_text(angle = 35, vjust = 0.6),
+      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
+      legend.position = "bottom"
+    )
+
+```
+
+------------------------------------------------------------------------
+
 # Supporting Information

### 2022-09-20 manuscript/manuscript.qmd
Add text in the methods.

@@
 
+The overview of ICLF systems in Brazil will be performed by analyzing published research and web surveys with experts.
+
 #### Literature review
 
+The literature review will be performed over published research from two sources, Scopus and Embrapa.
+It will have a very general approach, in which any research analyzing any aspect of ICLF will be screened.
+The strings that will be used to search research are the following:
+
+*   Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril) AND PUBYEAR > 1999
+
+* Embrapa: ((ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)) AND (ano-publicacao:[2000 TO *]) AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP" OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT") AND (idioma:"Inglês" OR idioma:"Português")
+
+The data and information extract from selected research will be diverse, and will be organized in 11 relational tables.
+The tables will cover general information about the research document and characteristics of the experiment, as also data about the system management, soil properties, productivity, growth, emissions, and radiation.
+All tables will be described by metadata files.
+
+An important assumption of the review is that the ICLF experiments are representative of the ICLF being implemented by farmers in Brazil.
+
 #### Experts survey
+
+The experts survey will be performed by a web application where the participants will be able to interact with a questionnaire to provide information about ICLF systems.
+
+The nature of the survey is semi-structured, with closed and open questions. The participants will have the option to avoid answering any question.
+
+The participants desired profile is of researchers or technicians with any experience with ICLF systems. A minimum of 50 participants is expected.
+
+The objective of the survey is to gather information that are not available in the literature, as also to provide expected scenarios to the ICLF expansion in the future.
+
+All answers will be stored in tables for posterior analysis. Each question will be represented by a column, and each participant will be represented as a row (one observation for each question).
+
+The web application will be deployed in a personal website, where the participants will receive the link of the survey, along with a token that will be used to submit the answers.
 

### 2022-09-23 manuscript/manuscript.qmd
Add text to the methods section.

@@
 
-The data and information extract from selected research will be diverse, and will be organized in 11 relational tables.
+The data and information extract from selected research will be diverse, and will be organized in 11 [relational tables](../iclfs_review/tables/00_tables_collection.html).
 The tables will cover general information about the research document and characteristics of the experiment, as also data about the system management, soil properties, productivity, growth, emissions, and radiation.
@@
 
+Model projections will estimate emissions and removals of Greenhouse Gases (GHG), food and fiber productivity and income of ICLF systems.
+The projections will be performed by a mixed modelling framework, using random processes, empirical and mechanistic models, deterministic and probabilistic factors to estimate the variables of interest.
+
+The projections will cover the whole Brazilian territory, from 2020 to 2100. Estimations will be made over a grid formed by 3x3 kilometers cells.
+
+The model will assume that ICLF will only occupy areas considered as degraded pasture according to the classification performed by MapBiomas [@Souza_2020].
+Another assumption is that after a transition from degraded pasture to ICLF, it will never change to another use.
+
 #### Projections scenarios
+
+To conduct the projections, a set of possible scenarios will be created. The scenarios will be based on data and information gathered from the systematic review and the experts survey.
+
+The ICLF expansion scenarios will be based on the expectations of experts, and will provide data to create three scenarios.
+One will be the median of the expected area to be occupied by ICLF in 2030, 2050 and 2100, the other two will be the upper and lower quartiles.
+These three scenarios will be considered as reasonable future projections.
+There are going to be other two extreme scenarios, one where there wont be any expansion of ICLF, and another where the ICLF will cover all the degraded pasture extent by 2100.
+
+The ICLF management scenarios will be based on the systematic review and experts survey.
+The management scenarios will dictate the characteristics of the ICLF systems being implemented in the future, as the species, population, spacing, inputs, and cycle length.
+The management scenarios will depend on the region where the ICLF system is being implemented.
 
@@
          nodesep = 2, 
-         ranksep = 0.4,
+         ranksep = 0.5,
          tooltip = ' ']
@@
 
-#### LULC projections
+#### Land use projections
+
+The land use projections will be performed by randomly assigning grid cells occupied by degraded pastures to be converted to ICLF.
+The assigned grid cell will first be occupied by a transition state, which will be a Integrated Crop Livestock (ICL) system, and after a certain period, it will finally change to a ICLF.
+The assigned cells will also be attributed with management characteristics from the management scenarios explained in the section above.
+
+The rate of ICLF expansion from year to year will be closely linear, and will be dictated by the ICLF expansion scenario.
+
+The ICLF expansion process will be repeated 100 times for each ICLF expansion scenario, providing a range of outcomes in the final results.
 
@@
 
-grViz(height = 500,
+grViz(
   "digraph {

### 2022-09-27 manuscript/manuscript.qmd
Add text on the benefits estimation section.

@@
 
+Three types of benefits will be estimated: carbon sequestration, food and fiber production, and economic revenue.
+
+Carbon sequestration will account for above and below ground.
+
+The above ground carbon will be calculated by estimates of tree growth and litter accumulation, and will be based on empirical models (ordinary least squares linear regression).
+The above ground carbon accumulation will be dependent on climatic variables, the species used in the ICLF system, and the population of each component of the integrated system.
+
+The below ground carbon will be calculated using a modelling framework proposed by @Sierra_2012.
+It is a flexible framework based on a general model of soil organic matter decomposition [@Sierra_2012].
+An implementation of the Century model [@Parton_1987] will be used to simulate organic matter decomposition along time.
+The soil carbon accumulation will be calculated by the amount of biomass input from the ICLF components over time.
+The decomposition will be affected by precipitation, temperature, potential evapotranspiration and soil texture.
+
 ```{r}

### 2022-09-27 manuscript/manuscript.qmd
Add text to the methods section.

@@
 
-The above ground carbon will be calculated by estimates of tree growth and litter accumulation, and will be based on empirical models (ordinary least squares linear regression).
+The above ground carbon will be calculated by estimates of tree growth and litter accumulation, and will be based on empirical models (ordinary least squares linear regression or random forest).
 The above ground carbon accumulation will be dependent on climatic variables, the species used in the ICLF system, and the population of each component of the integrated system.
@@
 The decomposition will be affected by precipitation, temperature, potential evapotranspiration and soil texture.
+
+The food and fiber productivity will be calculated separately for each component of ICLF. The components are the trees, the annual crops, the pasture and the livestock.
+
+The estimations of productivity will be performed by empirical models (ordinary least squares linear regression or random forest).
+They will be based on data gathered from the systematic review, and will be dependent on climatic variables, species used in each component, and the population numbers.
+
+The economic revenue estimations will account for costs and income related to the ICLF implementation.
+
+The costs to implement the ICLF systems will be based on management practices gathered by the systematic
+review, as also external sources when necessary.
+The income will be calculated over the productivity of each component of the ICLF system.
+The prices off inputs and outcomes will be corrected by inflation projections.
 
@@
 ### Critical analysis
+
+The critical analysis will expand the interpretation of the suitability of the expansion of ICLF as a mean to curb global warming. This will be done by putting the ICLF in context of some subjects:
+
+* The impact of the ICLF expansion in Brazil is important when comparing it with estimations of gross national emissions? What are the areas where the ICLF can actually help in decreasing emissions?
+
+* What are possible social impacts of the stimulation of ICLF adoption? Will it decrease social inequality in rural areas? Will it play a role in mitigating damage caused by climate change?
+
+* Nature based solutions or human based solutions? Do they complement each other or do they compete?
+
+* What are the consequences of focusing on increasing carbon removals rather than decreasing gross emissions? And how is this being addressed in public policies.
+
+To discuss the points above, a targeted review will be performed.
+The targeted review will be conducted by actively searching for digital content of various nature to seek information about the questions.
+It contrasts the systematic review since there will be no formal strategy of literature search.
+
+The use of a narrative discussion will expand the scope of the project, avoiding to drawn all the conclusions solely on quantitative estimates, and to put all the generated results in contexts of a bigger scenario.
 

### 2023-02-06 iclfs_forms/form.R
Remove files from old project.

@@ -1,452 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:        Form pilot
-# Description:
-#
-# Author:       Hugo Tameirao Seixas
-# Contact:      tameirao.hugo@gmail.com
-# Date:         2021-09-02
-#
-# Notes:
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(geobr)
-library(sf)
-library(ggplot2)
-library(readr)
-library(dplyr)
-library(shiny)
-library(shinythemes)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-fields_mandatory <- c("token")
-#tokens <- read_lines(here::here("iclfs_forms/tokens.txt"))
-tokens <- c("p023ru", "81lSDi4")
-#
-# LOAD BACKGROUND DATA -------------------------------------------------------
-
-## Load geobr states ----
-states <- read_state()
-states <- cbind(states, st_coordinates(st_centroid(states)))
-states_names <- pull(states, abbrev_state)
-
-
-# SHINY APP UI ----------------------------------------------------------------
-
-ui <-
-  fluidPage(
-
-    shinyjs::useShinyjs(),
-
-    ## Theme ----
-    theme = shinytheme("flatly"), # Set theme
-
-    ## Title ----
-    titlePanel("Perspectivas para o avanço do ILPF"),
-
-    navlistPanel(
-      widths = c(3, 9),
-
-      ## Introduction ----
-      tabPanel(
-        "Introdução",
-        h3("Introdução"),
-        p(
-          "Esse é o modelo do questionário que será utilizado nesse projeto."
-        ),
-        br(),
-        p(
-          "A seção de introdução vai ser responsável por esclarecer o objetivo
-          do projeto, o contexto em que as perguntas serão feitas,
-          e o guia de preenchimento do questionário."
-        )
-      ),
-
-      ## Question 01: ICFLS area projection ----
-      tabPanel(
-        "Questão 01",
-        sidebarLayout(
-          fluid = TRUE,
-          sidebarPanel( # Inputs panel
-            width = 10,
-            titlePanel(
-              title = "Segundo suas expectativas, qual a área total ocupada
-              por ILPF em 2030 e 2050, em milhões de hectares?"
-            ),
-            sliderInput( # Ask projected area for 2030
-              "area2030",
-              "Área total em 2030 (em milhões de hectares)",
-              value = 1,
-              min = 1,
-              max = 80
-            ),
[…]

### 2023-02-06 iclfs_projections/01_download_mapbiomas.R

@@ -1,31 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:
-# Description:
-#
-#
-#
-# Authors:      Hugo Tameirao Seixas
-# Contact:      seixas.hugo@protonmail.com
-# Date:         2022-07-07
-#
-# Notes:
-#
-#
-#
-#
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(rgee)
-library(sf)
-library(geobr)
-library(terra)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-#
-#

### 2023-02-06 iclfs_projections/03_download_soil.R

@@ -1,30 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:
-# Description:
-#
-#
-#
-# Authors:      Hugo Tameirao Seixas
-# Contact:      seixas.hugo@protonmail.com
-# Date:         2022-07-07
-#
-# Notes:
-#
-#
-#
-#
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(sf)
-library(geobr)
-library(terra)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-#
-#

### 2023-02-06 iclfs_projections/04_run_model.R

@@ -1,201 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:
-# Description:
-#
-#
-#
-# Authors:      Hugo Tameirao Seixas
-# Contact:      seixas.hugo@protonmail.com
-# Date:         2022-07-07
-#
-# Notes:
-#
-#
-#
-#
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(terra)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-#
-# LOAD BASE GRID --------------------------------------------------------------
-
-## Load raster file
-r <- rast("iclfs_projections/data/base_grid_pasture.tif")
-
-# GENERATE RANDOM DATA AS DUMMIES ---------------------------------------------
-
-## Generate random system types to be sampled
-systems <-
-  reduce(
-    map2(
-      .x = c(2, 3, 4, 5, 6),
-      .y = sample(1:30, 5, replace = TRUE),
-      .f = ~ { rep(.x, .y) }),
-    c
-  )
-
-## Generate random cycle lengths to be sampled
-cycle <-
-  reduce(
-    map2(
-      .x = c(10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20),
-      .y = sample(1:30, 11, replace = TRUE),
-      .f = ~ { rep(.x, .y) }),
-    c
-  )
-
-## Generate random transition system type to be sampled
-transition_systems <-
-  reduce(
-    map2(
-      .x = c(1, 2, 3, 4, 5, 6),
-      .y = sample(1:30, 6, replace = TRUE),
-      .f = ~ { rep(.x, .y) }),
-    c
-  )
-
-## Generate random transition lengths to be sampled
-transition_length <-
-  reduce(
-    map2(
-      .x = c(1, 2, 3, 4),
-      .y = sample(1:30, 4, replace = TRUE),
-      .f = ~ { rep(.x, .y) }),
-    c
-  )
-
-## Generate random trees population/ha to be sampled
-tree_pop <-
-  reduce(
-    map2(
-      .x = c(333, 400, 476, 500, 370, 690, 715, 900, 1292),
-      .y = sample(1:40, 9, replace = TRUE),
-      .f = ~ { rep(.x, .y) }),
-    c
-  )
-
-## Generate ICLFS management to be sampled
-system_management <-
-  reduce(
-    map2(
[…]

### 2023-02-06 iclfs_projections/R/ilpf_biomass.R

@@ -1,2 +1,0 @@
-
-# Functions to calculate biomass from ILPF

### 2023-02-06 iclfs_projections/R/ilpf_carbon.R

@@ -1,2 +1,0 @@
-
-# Functions to calculate carbon from ILPF

### 2023-02-06 iclfs_projections/R/ilpf_expansion.R

@@ -1,64 +1,0 @@
-
-for (y in 2021:2050) {
-
-  sample_pool <- lulc %>%
-    filter(
-      year == y - 1,
-      cover == 1
-    )
-
-  sample <- sample_pool %>%
-    sample_frac()
-
-  sample_sub <- sample %>%
-    mutate(area_sum = cumsum(area)) %>%
-    filter(area_sum < annual_increase + 10)
-
-  new_system <- sample(systems, size = number_of_rows, replace = TRUE)
-
-  new_cycle <- sample(cycle, size = number_of_rows, replace = TRUE)
-
-  new_transition <- sample(transition_systems, size = number_of_rows, replace = TRUE)
-
-  new_transition_length <- sample(transition_length, size = number_of_rows, replace = TRUE)
-
-  new_tree_pop <- sample(tree_pop, size = number_of_rows, replace = TRUE)
-
-  new_system_management <- sample(system_management, size = number_of_rows, replace = TRUE)
-
-  new_transition_management <- sample(transition_management, size = number_of_rows, replace = TRUE)
-
-  new_year <- lulc %>%
-    filter(year == y - 1) %>%
-    mutate(
-      year = y,
-      new_cover = new_system,
-      new_cycle = new_cycle,
-      new_transition = new_transition,
-      mew_transition_length = new_transition_length,
-      new_tree_pop = new_tree_pop,
-      new_system_management = new_system_management,
-      new_transition_management = new_transition_management,
-      transition = if_else(cell %in% sample_sub$cell, new_transition, transition),
-      transition_length = if_else(cell %in% sample_sub$cell, new_transition_length, transition_length),
-      cover = if_else(cell %in% sample_sub$cell, new_system, cover),
-      cycle_lenght = if_else(cell %in% sample_sub$cell, new_cycle, cycle_lenght),
-      cycle_end = if_else(cell %in% sample_sub$cell, year + cycle_lenght + transition_length, cycle_end),
-      tree_pop = if_else(cell %in% sample_sub$cell, new_tree_pop, tree_pop),
-      system_management = if_else(cell %in% sample_sub$cell, new_system_management, system_management),
-      transition_management = if_else(cell %in% sample_sub$cell, new_transition_management, transition_management)
-    )
-
-  new_year <- new_year %>%
-    mutate(
-      cover = if_else(cycle_end - year == 0, new_system, cover, missing = cover),
[…]

### 2023-02-06 iclfs_projections/R/ilpf_income.R

@@ -1,2 +1,0 @@
-
-# Functions to calculate income from ILPF

### 2023-02-06 iclfs_projections/R/ilpf_productivity.R

@@ -1,2 +1,0 @@
-
-# Functions to calculate productivity from ILPF

### 2023-02-06 iclfs_review/review_data_manager.R

@@ -1,1478 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title: Review Data Manager
-# Description:
-#
-#
-#
-# Authors:      Hugo Tameirao Seixas
-# Contact:      tameirao.hugo@gmail.com
-# Date:         2022-07-14
-#
-# Notes:
-#
-#
-#
-#
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(fs)
-library(magrittr)
-library(gt)
-library(glue)
-library(tidyverse)
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-#
-# CREATE LITERATURE SEARCH METADATA -------------------------------------------
-
-bind_rows(
-  list(
-    database = "Scopus",
-    database_url = "https://www.scopus.com/",
-    search_string = glue(.sep = " ",
-      "TITLE-ABS-KEY(",
-      "iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest",
-      "OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR",
-      "agrosilvipastoril) AND PUBYEAR > 1999"
-    ),
-    oldest_publication_date = 2007,
-    newest_publication_date = 2022
-  ),
-  list(
-    database = "Embrapa",
-    database_url = "https://www.bdpa.cnptia.embrapa.br/consulta/busca",
-    search_string = glue(.sep = " ",
-      '((ICLF) OR (iclfs) OR (crop-livestock-forestry)',
-      'OR (crop-livestock-forest) OR (agrosilvipastoral)',
-      'OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril))',
-      'AND (ano-publicacao:[2000 TO *])',
-      'AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP"',
-      'OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT")',
-      'AND (idioma:"Inglês" OR idioma:"Português")'
-    ),
-    oldest_publication_date = 2000,
-    newest_publication_date = 2022
-  )
-) %>%
-  rename_with( ~ str_replace_all(., "_", " ")) %>%
-  gt() %>%
-  tab_header(title = "LITERATURE SEARCH") %>%
-  tab_options(
-    heading.background.color = "#d2d2d2",
-    table.border.top.width = 3,
-    table.border.top.color = "#666663",
[…]

### 2023-02-06 manuscript/lct_se_ac.qmd
Add new files.

---
title: "Dimensions of the impacts of land transitions in the Amazon and Cerrado"
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
format: 
  html:
    theme: lux
page-layout: article
bibliography: references.bib
link-citations: true
editor: visual
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto
  cache: true
license: CC BY-NC-ND 4.0
---

```{r}
#| include: false

library(sf)
library(geobr)
library(gt)
library(DiagrammeR)
library(lubridate)
library(tidyverse)

```

## Introduction

## Objectives

The present work is composed of  three main objectives, accompanied by related questions:

1.  Predict probability and area of native vegetation suppression in the Amazon and Cerrado;
    a.  What are the main drivers of native vegetation suppression?
    b.  How do drivers interact among them?
2.  Predict land cover transition trajectories after native vegetation suppression;
    a.  What are the main drivers of land cover dynamics after native vegetation suppression?
    b.  How do drivers interact among them?
    c.  What are the main patterns for future projections in the Amazon and Cerrado?
3.  Predict the impact of land cover transitions over environmental and social variables;
    a.  What is the importance of land cover transitions in predicting environmental and social variables?
    b.  Does land-use transitions interact with other drivers of environmental and social variables?
    c.  What are the expected social and environmental projections in different land-cover trajectories for the near future?

## Materials and Methods

To achieve the proposed goal, I will divide the work into three major parts:

1.  Literature overview of the main drivers of the expected outcomes (vegetation suppression, land cover transition, social and environmental variables);

2.  Screening for available data and development of structured data collection;

3.  Development of models;

4.  Future projections;

```{r}
#| echo: false

grViz(
  "digraph {

  graph [layout = dot, 
         rankdir = TD, 
         nodesep = 1.5, 
         ranksep = 1.0,
         tooltip = ' ']

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  edge [penwidth = 2.5, 
        arrowsize = 2,
        tooltip = ' ']

  a [label = 'Literature \n Review', xlabel = '1']
  b [label = 'Experts Survey', xlabel = '1']
  c [label = 'Available Data', xlabel = '2']
  d [label = 'Database \n Structuring', xlabel = '2']
  e [label = 'Models \n Development', xlabel = '3']
  f [label = 'Projections \n Scenarios', xlabel = '4']
  g [label = 'Projections \n Estimations', xlabel = '4']

  a -> c a -> d
  c -> d b -> d
  b -> e b -> f
  e -> g f -> g
  d -> e

  }"
)

```

#### Literature Overview

The literature overview will be performed over different subjects.

#### Database Structuring

The database will contain data from different themes. To structure a collection of data which presents different nature, I will transform them into a common grid system. The grid system will be composed by 0.3 degrees cells.

```{r}
#| echo: false
#| message: false

biomes <- read_biomes(showProgress = FALSE) %>%
  filter(name_biome %in% c("Amazônia", "Cerrado")) %>%
  st_make_valid()

grid <- 
  st_make_grid(biomes, cellsize = 0.3) %>%
  st_as_sf() %>%
  st_filter(biomes, .predicate = st_intersects)

ggplot() +
  geom_sf(data = biomes) +
  geom_sf(data = grid, fill = "transparent") +
  theme_void()

```

#### Model Development

The models will follow a sequential order. The output of a model will serve as a feature to the next model.

```{r}
#| echo: false

table <-
  tibble(
    section = c(
      "Vegetation suppression probability", "Vegetation suppression area", 
      "Land cover transitions", "Transitions impacts"
    ),
    model_type = c(
      "Classification", "Regression",
      "Classification", "Regression"
    )
  )

table %>%
  pivot_wider(names_from = section, values_from = model_type) %>%
  gt() %>%
  cols_align(align = "center") %>%
  tab_options(
    table.border.top.style = "hidden",
    table.border.bottom.style = "hidden"
  )

```

The first model will classify areas that suffered vegetation suppression. So the outcome will be a binary result (0 = no suppression; 1 = suppression). I want that this model to have the minimum inclusion errors for the class "1". In other words, I want to avoid, as best as I can, classifying an area with label "1", when the reality is that the area should be label "0". To achieve this, the model will be adjusted to present the minimum inclusion error for the class "1", and the probability threshold for class "1" will be a higher value.

The second model will predict the amount of vegetation suppression that was classified with the label "1" in the previous model. The predictions will have to be bounded by the amount of natural vegetation inside the grid cell.

The third model will predict the predominant land use transitions of the areas that suffered native vegetation suppression.

The fourth model will be actually a set of models. Each model will be responsible to predict environmental and social outcomes from land transition patterns.

## Results

## Discussion

## Conclusions

## Schedule

```{r}
#| echo: false
#| warning: false

schedule_table <- 
  bind_rows(
    list(
      activity = "Literature Review",
      start = "01-02-2023",
      end = "01-06-2023",
      section = 1
    ),
    list(
      activity = "Experts Survey",
      start = "01-06-2023",
      end = "01-01-2024",
      section = 1
    ),
    list(
      activity = "Data Screening",
      start = "01-02-2023",
      end = "01-08-2023",
      section = 2
    ),
    list(
      activity = "Database Structuring",
      start = "01-04-2023",
      end = "01-09-2023",
      section = 2
    ),
    list(
      activity = "Exploratory Data Analisys",
      start = "01-06-2023",
      end = "01-11-2023",
      section = 2
    ),
    list(
      activity = "Models Development",
      start = "01-11-2023",
      end = "01-05-2024",
      section = 3
    ),
    list(
      activity = "Projections Estimations",
      start = "01-05-2024",
      end = "01-09-2024",
      section = 4
    )
  )

schedule_table <- schedule_table %>%
  mutate(
    start = dmy(start),end = dmy(end),
    activity = factor(activity, levels = activity)
  ) %>%
  pivot_longer(
    cols = c(start, end),
    names_to = "when",
    values_to = "date"
  )

schedule_table %>%
    ggplot() +
    geom_line(
      aes(x = date, y = activity), 
      linewidth = 3, 
      lineend = "round"
    ) +
    scale_y_discrete(limits = rev) +
    scale_x_date(
      date_labels = "%b-%Y", 
      date_breaks = "6 months", 
      date_minor_breaks = "1 month",
      limits = c(ymd("2022-09-01"), ymd("2025-03-01"))
    ) +
    labs(color = "Section") +
    theme_minimal() + 
    theme(
      text = element_text(family = "sans", size = 15),
      panel.grid.major = element_line(color = "#a9a9a9"),
      axis.title = element_blank(),
      axis.text.x = element_text(angle = 35, vjust = 0.6),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
      legend.position = "bottom"
    )

```

## References

### 2023-02-07 manuscript/lct_se_ac.qmd
Add content to the literature review methods.

@@
 link-citations: true
-editor: visual
 editor_options: 
@@
   freeze: auto
-  cache: true
 license: CC BY-NC-ND 4.0
@@
          rankdir = TD, 
-         nodesep = 1.5, 
-         ranksep = 1.0,
+         nodesep = 1.2, 
+         ranksep = 0.8,
          tooltip = ' ']
@@
 
-The literature overview will be performed over different subjects.
+The literature overview will be performed over different subjects. For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
+
+```{r}
+#| echo: false
+
+grViz(
+  "digraph {
+
+  graph [layout = dot, 
+         overlap = false,
+         rankdir = TB, 
+         nodesep = 5, 
+         ranksep = 0.4,
+         tooltip = ' ']
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
+
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
+
+  a [label = 'Specific \n Questions']
+  b [label = 'Query \n Development']
+  c [label = 'Database Search']
+  d [label = 'Documents \n Screening']
+  e [label = 'Documents \n Collection']
+  f [label = 'Forward Snowball \n Search']
+  g [label = 'Final Collection']
+
+  a -> b a -> d
+  b -> c c -> d
+  d -> e e -> f
+  f -> d e -> g
+
+  }"
+)
+
+```
 
@@
 
-The models will follow a sequential order. The output of a model will serve as a feature to the next model.
+The models will follow a sequential order.
+The output of a model will serve as a feature to the next model.
 
@@
 
-The fourth model will be actually a set of models. Each model will be responsible to predict environmental and social outcomes from land transition patterns.
+The fourth model will be actually a set of models.
+Each model will be responsible to predict environmental and social outcomes from land transition patterns.
 

### 2023-02-07 manuscript/lct_se_ac.qmd
Add content to the whole manuscript.

@@
   freeze: auto
+  cache: true
 license: CC BY-NC-ND 4.0
@@
 
-#### Literature Overview
+\
 
-The literature overview will be performed over different subjects. For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
+The literature review will provide a theoretical and practical basis for the modelling section.
+
+The database structuring will store all the relevant data in a single file structure, so that the modelling section can be performed in a clean and organized manner.
+
+The models will be developed following standard procedures and libraries that allow the implementation of different techniques. Each model will be stored as a mean to be reproduced when needed.
+
+Future projections will serve as a bridge to discuss how public policies can be planned to mitigate negative impacts of native vegetation suppression in the Amazon and Cerrado.
+
+#### Literature Review
+
+The literature review will be performed over different subjects. For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
 
@@
 
+\
+
+The literature review will serve to answer questions about variables that will be predicted in this project.
+For each variable, I want to explore what are the main drivers that are causing them, how these drivers relate with each other, and what were the methods used to estimate the effects and interactions.
+
 #### Database Structuring
@@
 ```
+
+Each grid cell will contain an observation, for each year, for all the variables that will be included in the study.
 
@@
 
+The study will provide three main quantitative results, predictions of vegetation suppression, predictions of land use transitions, and predictions of social and environmental variables.
+
+More than only the predictions, I will also analyse and present explanations of the models behavior, and inferences about the studied phenomena (will only take this leap if I feel confident with the models).
+
 ## Discussion
+
+The discussion of the results will focus on two fronts, comparing our results with previous studies, and build a bridge with discussions from social sciences and political science.
 

### 2023-02-07 manuscript/lct_se_ac.qmd
Start introduction.

@@
 
+Analysis of the drivers and impacts of native vegetation suppression in Brazil is not new.
+However, the approaches used to analyse this phenomena usually focus in few dimensions.
+I propose creating a modelling framework, using modern techniques, to predict and explain native vegetation suppression and its impacts on social and environmental variables.
+The study will also analyse the Amazon and Cerrado at the same time, and will explore whether predictions from one biome are related to predictions from the other biome.
+
 ## Objectives
@@
     c.  What are the expected social and environmental projections in different land-cover trajectories for the near future?
+    d.  Do predictions from both biomes show relation between each other?
 

### 2023-02-09 manuscript/lct_se_ac.qmd
Add more content.

@@
 license: CC BY-NC-ND 4.0
+self-contained: true
 ---
@@
 ```{r}
+#| label: libraries
 #| include: false
@@
 
-Analysis of the drivers and impacts of native vegetation suppression in Brazil is not new.
-However, the approaches used to analyse this phenomena usually focus in few dimensions.
+Analyzing the drivers and impacts of native vegetation suppression is a complex task.
+The amount of factors influencing both phenomena can be numerous and heterogeneous.
+Existing literature suggests that native vegetation suppression can be caused by economic fluctuations [@hargrave-2012], conservation policies [@pfaff-2015], population distribution [@jusys-2016], land tenure [@cattaneo-2001], livestock and crop productions [@bowman-2016].
+By the other side, vegetation removed is believed to impact human health [@santos-2018], climate regime [@silva-2023], regional hydrology [@cavalcante-2019], soil properties [@dias-2022], biodiversity [@gestich-2021].
+
+Usually, the studies analyzing both phenomena focus in few variables, and normally struggle to relate their results to other areas of knowledge.
+
 I propose creating a modelling framework, using modern techniques, to predict and explain native vegetation suppression and its impacts on social and environmental variables.
@@
 
+An important aspect of the objectives, is that they are bound to the model behavior.
+This means that the results will not necessarily describe the phenomena in the real world, and this leap should be done with extreme care.
+This is true for any type of model developed to explain the reality.
+
 ## Materials and Methods
 
-To achieve the proposed goal, I will divide the work into three major parts:
+To achieve the proposed goal, I will divide the work into four major parts:
 
@@
 ```{r}
+#| label: method-diagram
 #| echo: false
@@
 The literature review will provide a theoretical and practical basis for the modelling section.
+Information about what variables are being used, how are they being manipulated, what are the analysis techniques used to reach the results.
 
@@
 ```{r}
+#| label: lit-review-diagram
 #| echo: false
@@
 ```{r}
+#| label: grid-map-figure
 #| echo: false
@@
 
+```{r}
+#| label: database-diagram
+#| echo: false
+#| message: false
+
+grViz(
+  "digraph {
+
+  graph [layout = dot, 
+         overlap = false,
+         rankdir = TB, 
+         nodesep = 1.4, 
+         ranksep = 0.8,
+         tooltip = ' ']
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
+
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
+
+  a [label = 'Data Source']
+  b [label = 'Data Source']
+  c [label = 'Data Source']
+  d [label = 'Data Source']
+  e [label = 'Pre Processing']
+  f [label = 'Gridded Data']
+  g [label = 'Database']
+
+  a -> e b -> e
+  c -> e d -> e
+  e -> f f -> g
+
+  }"
+)
+
+```
+
+The data will be stored in a nested directories structured database, using give-style partitioning.
+The database will be composed by a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
+
 #### Model Development
@@
 ```{r}
+#| label: model-table
 #| echo: false
@@
 
+Each model will follow the standard approach to develop supervised models.
+
+```{r}
+#| label: model-diagram
+#| echo: false
+#| message: false
+
+grViz(
+  height = 800,
+  "digraph {
+
+  graph [layout = dot, 
+         overlap = false,
+         rankdir = TD, 
+         nodesep = 1.8, 
+         ranksep = 0.5,
+         tooltip = ' ']
+
+  node [shape = box,
+        fontname = Helvetica,
+        style = filled,
+        fontcolor = '#343a40'
+        fillcolor = '#f7f7f9'
+        penwidth = 2.5,
+        width = 3,
+        height = 1.2,
+        fontsize = 25,
+        tooltip = ' ']
+
+  edge [penwidth = 2.5, 
+        arrowsize = 2,
+        tooltip = ' ']
+
+  a [label = 'Database']
+  b [label = 'Variables \n Selection']
+  c [label = 'Data Split']
+  d [label = 'Training Data']
+  e [label = 'Validation \n Data']
+  f [label = 'Test Data']
+  g [label = 'Pre Processing']
+  h [label = 'Initial \n Model Fit']
+  i [label = 'Parameters \n Adjustments']
+  j [label = 'Final \n Model Fit']
+  k [label = 'Model \n Assessment']
+  l [label = 'Model \n Interpretation']
+
+  a -> b b -> c
+  c -> d c -> e c -> f 
+  d -> g g -> h 
+  h -> i e -> i
+  i -> j j -> k f -> k
+  j -> l k -> l
+
+  }"
+)
+
+```
+
+\
+
+In order to interpret the models, a series of methods will be used to explain the predictions, such as surrogate models, feature interactions, permutation feature importance, counterfactual explanations and Shapley values.
+These are all model agnostic methods, so they can be applied in any kind of regression or classification models.
+
 ## Results
@@
 ## Conclusions
+
+The idea of the project is to advance the understanding of why vegetation removals are happening, and than how are they impacting the environment and human well being.
+This have potential to shed light of what can be done to mitigate negative effects after the vegetation removal occurs.
 

### 2023-02-09 manuscript/lct_se_ac.qmd
Add text to the whole document. Make some writing improvements.

@@
 
-Analyzing the drivers and impacts of native vegetation suppression is a complex task.
-The amount of factors influencing both phenomena can be numerous and heterogeneous.
-Existing literature suggests that native vegetation suppression can be caused by economic fluctuations [@hargrave-2012], conservation policies [@pfaff-2015], population distribution [@jusys-2016], land tenure [@cattaneo-2001], livestock and crop productions [@bowman-2016].
-By the other side, vegetation removed is believed to impact human health [@santos-2018], climate regime [@silva-2023], regional hydrology [@cavalcante-2019], soil properties [@dias-2022], biodiversity [@gestich-2021].
+The suppression of native vegetation in the Cerrado and Amazon biomes is a matter of great concern due to its potential impact on the environment and human well-being. 
+Understanding the drivers and effects of this phenomenon is crucial to guide policies to avoid natural vegetation suppression and mitigate negative impacts.
+However, this is a challenging task since the factors involved in this phenomenon are diverse, heterogeneous, and can even be contradictory. 
+Existing literature suggests that native vegetation suppression is caused by economic fluctuations [@hargrave-2012], conservation policies [@pfaff-2015], population distribution [@jusys-2016], land tenure [@cattaneo-2001], livestock and crop productions [@bowman-2016].
+On the other side, vegetation removal may impact human health [@santos-2018], climate regime [@silva-2023], regional hydrology [@cavalcante-2019], soil properties [@dias-2022], biodiversity [@gestich-2021].
 
-Usually, the studies analyzing both phenomena focus in few variables, and normally struggle to relate their results to other areas of knowledge.
+Unfortunately, much of the research in this area tends to focus on only a few dimensions of the problem, rather than taking a holistic approach.
+This narrow focus often fails to capture the full extent of the issue and can lead to oversimplifications or misdirection in efforts to solve it.
 
-I propose creating a modelling framework, using modern techniques, to predict and explain native vegetation suppression and its impacts on social and environmental variables.
-The study will also analyse the Amazon and Cerrado at the same time, and will explore whether predictions from one biome are related to predictions from the other biome.
+The objective of this project is to create a modelling framework, designed to  predict and understand the causes and impacts of native vegetation suppression in the Cerrado and Amazon biomes, considering environmental and anthropic dimensions.
+The project aims to develop a deeper understanding of the relationships between land use changes, environmental factors, and social dynamics related to the suppression of native vegetation.
+
+To achieve the objective, regression and classification models will be applied to existing data on land use changes, environmental factors, and social variables in the Cerrado and Amazon biomes. 
+The models will be used to identify patterns and relationships between these variables, and to predict future trends.
+
+The results of this project will contribute to a better understanding of the causes and impacts of native vegetation suppression in the Cerrado and Amazon biomes. 
+This knowledge will inform the development of effective conservation and management strategies that will help to protect these vital and unique ecosystems.
 
@@
 
-An important aspect of the objectives, is that they are bound to the model behavior.
-This means that the results will not necessarily describe the phenomena in the real world, and this leap should be done with extreme care.
-This is true for any type of model developed to explain the reality.
+The three objectives, in conjunction, will provide an in-depth analysis of what can be done to avoid native vegetation suppression, and how to mitigate its negative impacts.
 
@@
 
+The study will rely on the use of available data to develop regression and classification models that will predict native vegetation suppression and its impacts. 
 To achieve the proposed goal, I will divide the work into four major parts:
@@
 The literature review will provide a theoretical and practical basis for the modelling section. 
-Information about what variables are being used, how are they being manipulated, what are the analysis techniques used to reach the results.
+Information about what variables are being used, how are they being manipulated, and what are the analysis techniques used to reach the results.
 
@@
 
-The models will be developed following standard procedures and libraries that allow the implementation of different techniques. Each model will be stored as a mean to be reproduced when needed.
+The models will be developed following standard procedures and libraries that allow the implementation of different techniques. 
+The choice of models will be done after a series of tests, and will depend on the accuracy and the adequacy to the theory. Each model will be stored as a mean to be reproduced when needed.
 
@@
 
-The literature review will be performed over different subjects. For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
+The literature review will be performed over different subjects. 
+For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
 
@@
 
-The database will contain data from different themes.
-To structure a collection of data which presents different nature, I will transform them into a common grid system.
-The grid system will be composed by 0.3 degrees cells.
+The database will contain data from different domains, which can be available in different formats and structures.
+It is vital that all variables of interests are organized in a coherent manner, so that the modelling process can be more efficient and transparent.
+To structure a collection of data which presents different nature, I will transform all the variables to fit into a common grid system.
+The grid system will be composed by 0.2 degrees cells (40km x 40km), which should be a balanced compromise between detail and computational cost.
 
@@
 grid <- 
-  st_make_grid(biomes, cellsize = 0.3) %>%
+  st_make_grid(biomes, cellsize = 0.2) %>%
   st_as_sf() %>%
@@
 Each grid cell will contain an observation, for each year, for all the variables that will be included in the study. 
+Only pixels that contained natural vegetation at the first year of the analysis will be considered valid.
+
+The process to create the database will consist of accessing the data sources, download the data to the local environment, transform and organize the data to the common grid (if the data source provides any kind of pre-processing tool before download the data, it should be done that way), and store in the local environment.
 
@@
 The database will be composed by a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
+The basic partition will be the variables, which means that each variable will be stored in a separated directory.
+If necessary, the data will be partitioned by further variables (as a rule of thumb, each parquet file should not be smaller than 20MB and not bigger than 2GB).
 
@@
 In other words, I want to avoid, as best as I can, classifying an area with label "1", when the reality is that the area should be label "0".
-To achieve this, the model will be adjusted to present the minimum inclusion error for the class "1", and the probability threshold for class "1" will be a higher value.
+To achieve this, the model will be adjusted to present the minimum inclusion error for the class "1", and the probability threshold to classify an observation as class "1" will be a higher value.
 
 The second model will predict the amount of vegetation suppression that was classified with the label "1" in the previous model.
-The predictions will have to be bounded by the amount of natural vegetation inside the grid cell.
+The predictions will have to be bounded by the amount of natural vegetation inside the grid cell (a poisson distribution may be adequate to represent this variable).
 
@@
 The fourth model will be actually a set of models.
-Each model will be responsible to predict environmental and social outcomes from land transition patterns.
+Each model will be responsible to predict a single environmental or social outcome.
 
@@
 
-In order to interpret the models, a series of methods will be used to explain the predictions, such as surrogate models, feature interactions, permutation feature importance, counterfactual explanations and Shapley values.
-These are all model agnostic methods, so they can be applied in any kind of regression or classification models.
+To understand and interpret the predictions made by the models, I will employ a variety of methods to interpret prediction models.
+They may include surrogate models, feature interactions, permutation feature importance, counterfactual explanations, and Shapley values.
+These methods are model-agnostic, meaning they can be applied to any type of regression or classification model, regardless of its underlying structure or parameters.
+By using these techniques, I aim to gain a deeper understanding of the relationships between the variables and how they contribute to the predictions.
+This information will help to assess the reliability of the models and the validity of their results.
 
@@
 
-The study will provide three main quantitative results, predictions of vegetation suppression, predictions of land use transitions, and predictions of social and environmental variables.
+The study will present three main quantitative results based on quantitative data: predictions on vegetation suppression, land use transitions, and social and environmental variables. 
+Our predictions on vegetation suppression will show the likelihood and extent of removal events, serving as a basis for predicting the land use changes of the affected grid cells. 
+Finally, we will predict the impact of these findings on the environment and human well-being.
 
-More than only the predictions, I will also analyse and present explanations of the models behavior, and inferences about the studied phenomena (will only take this leap if I feel confident with the models).
+As part of the study, I will not only present the predictions generated by the models, but also perform an in-depth analysis of the models behavior. 
+This analysis will provide a deeper understanding of the underlying mechanisms that drive the predictions and help to assess their reliability and accuracy.
+Furthermore, based on my confidence in the models and their results, I will make inferences about the studied phenomena. 
+This will allow me to go beyond the mere presentation of the predictions and offer insights into the relationships between the variables, the causes of the observed patterns, and the implications of the results for the environment and human well-being.
+However, it is important to note that I will only take this step if I feel confident in the models and their results, as making inferences requires a strong foundation of knowledge and understanding.
 
@@
 
-The discussion of the results will focus on two fronts, comparing our results with previous studies, and build a bridge with discussions from social sciences and political science.
+In this study, I will be comparing the outcomes of my models, which are grounded in regression and classification predictive modeling, to the conclusions drawn from previous research that primarily utilized statistical inference and mechanistic models.
+My aim is to analyze the potential advantages and limitations of the methodology I have developed through this comparison.
+
+In addition to comparing the results of my models with previous research, I will also be exploring the practical implications of the findings.
+Specifically, I will be examining how the results can be used to inform and support decision making, particularly when dealing with complex environmental and human well-being issues that involve multiple dimensions.
+In many cases, decision making related to vegetation removals and their impact on the environment and human well-being can be challenging due to the multiple and sometimes conflicting factors that need to be considered.
+
+The findings can be used to identify the most significant factors that contribute to vegetation removals and their impact on the environment and human well-being, as well as how these factors interact with one another.
+This information can then be used to prioritize the most pressing issues and to design targeted interventions and strategies to mitigate the negative effects of vegetation removals.
 
@@
 
-The idea of the project is to advance the understanding of why vegetation removals are happening, and than how are they impacting the environment and human well being.
-This have potential to shed light of what can be done to mitigate negative effects after the vegetation removal occurs.
+The main objective of the project is to delve deeper into the reasons behind vegetation removals and to assess their impact on the environment and human well-being. 
+This effort has the potential to provide valuable insights into what can be done to reduce the negative consequences after the vegetation removal. 
+By thoroughly investigating the causes of vegetation removal and its effects, the project aims to contribute to a better understanding of this complex issue and to identify strategies for mitigating its negative impact.
+The end goal is to ensure that future vegetation removal is carried out in a way that minimizes harm to the environment and supports the well-being of people who depend on it.
 
@@
       start = "01-02-2023",
-      end = "01-06-2023",
+      end = "01-07-2023",
       section = 1

### 2023-02-09 manuscript/lct_se_ac.qmd
Improve text quality.

@@
 
-The objective of this project is to create a modelling framework, designed to  predict and understand the causes and impacts of native vegetation suppression in the Cerrado and Amazon biomes, considering environmental and anthropic dimensions.
-The project aims to develop a deeper understanding of the relationships between land use changes, environmental factors, and social dynamics related to the suppression of native vegetation.
+This project aims to predict and understand the causes and impacts of native vegetation suppression in the Cerrado and Amazon biomes, considering environmental and anthropic dimensions. 
+The results will provide a deeper understanding of the relationships between land use changes, environmental factors, and social dynamics related to native vegetation suppression.
 
-To achieve the objective, regression and classification models will be applied to existing data on land use changes, environmental factors, and social variables in the Cerrado and Amazon biomes. 
-The models will be used to identify patterns and relationships between these variables, and to predict future trends.
+Regression and classification models will be applied to existing data on land use changes, environmental factors, and social variables in the Cerrado and Amazon biomes. 
+The models will be used to identify patterns and relationships between these variables and to predict future trends.
 
@@
     c.  What are the expected social and environmental projections in different land-cover trajectories for the near future?
-    d.  Do predictions from both biomes show relation between each other?
+    d.  Do predictions from both biomes show a relation between each other?
 
-The three objectives, in conjunction, will provide an in-depth analysis of what can be done to avoid native vegetation suppression, and how to mitigate its negative impacts.
+The three objectives, in conjunction, will provide an in-depth analysis of how to avoid native vegetation suppression and mitigate its negative impacts.
 
@@
 
-The study will rely on the use of available data to develop regression and classification models that will predict native vegetation suppression and its impacts. 
+The study will rely on available data to develop regression and classification models to predict native vegetation suppression and its impacts. 
 To achieve the proposed goal, I will divide the work into four major parts:
@@
 
-The literature review will provide a theoretical and practical basis for the modelling section. 
-Information about what variables are being used, how are they being manipulated, and what are the analysis techniques used to reach the results.
+The literature review will provide a theoretical and practical basis for the modeling section. 
+Information about the key variables, their manipulation process, and the analysis techniques used to reach the results.
 
-The database structuring will store all the relevant data in a single file structure, so that the modelling section can be performed in a clean and organized manner.
+The database structuring will store all the relevant data in a single file structure to facilitate the modeling process.
 
-The models will be developed following standard procedures and libraries that allow the implementation of different techniques. 
-The choice of models will be done after a series of tests, and will depend on the accuracy and the adequacy to the theory. Each model will be stored as a mean to be reproduced when needed.
+The modeling process will follow standard procedures and libraries, with the possibility to implement different techniques.
 
-Future projections will serve as a bridge to discuss how public policies can be planned to mitigate negative impacts of native vegetation suppression in the Amazon and Cerrado.
+The choice of models will depend on a series of tests, accounting the accuracy and adequacy of the model to the theory.
+
+Future projections will serve as a bridge to discuss public policy planning to mitigate the negative impacts of native vegetation suppression in the Amazon and Cerrado.
 
@@
 
-The literature review will be performed over different subjects. 
-For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.
+The literature review will address different topics. 
+For all of them, I will adopt a hybrid approach of database searches combined with snowball searches.
 
@@
 
-The literature review will serve to answer questions about variables that will be predicted in this project. 
-For each variable, I want to explore what are the main drivers that are causing them, how these drivers relate with each other, and what were the methods used to estimate the effects and interactions.
+The literature review will answer questions about variables to be predicted in this project. 
+For each variable, I want to explore the main drivers that cause them, how they relate to each other, and the methods used to estimate the effects and interactions.
 
@@
 
-The database will contain data from different domains, which can be available in different formats and structures.
-It is vital that all variables of interests are organized in a coherent manner, so that the modelling process can be more efficient and transparent.
-To structure a collection of data which presents different nature, I will transform all the variables to fit into a common grid system.
-The grid system will be composed by 0.2 degrees cells (40km x 40km), which should be a balanced compromise between detail and computational cost.
+The database will contain data from different domains, which can be available in diverse formats and structures.
+To make the modeling process more efficient and transparent, all variables of interest must be organized coherently.
+To structure a collection of data that presents different natures, I will transform all the variables into a standard grid system.
+The grid system will be composed of 0.2 degrees cells (40km x 40km), which should be a balanced compromise between detail and computational cost.
 
@@
 
-Each grid cell will contain an observation, for each year, for all the variables that will be included in the study. 
-Only pixels that contained natural vegetation at the first year of the analysis will be considered valid.
+Each grid cell will contain an observation, for each year, for all the variables. 
+Only pixels that contained natural vegetation in the first year of the analysis will be considered valid.
 
-The process to create the database will consist of accessing the data sources, download the data to the local environment, transform and organize the data to the common grid (if the data source provides any kind of pre-processing tool before download the data, it should be done that way), and store in the local environment.
+The process to create the database will consist of accessing the data sources, downloading the data to the local environment, transforming and organizing the data to the grid (if the data source provides any pre-processing tool before downloading the data, it should be done that way), and store in the local environment.
 
@@
 
-The data will be stored in a nested directories structured database, using give-style partitioning. 
-The database will be composed by a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
-The basic partition will be the variables, which means that each variable will be stored in a separated directory.
+The data will be stored in a nested directories structured database with hive-style partitioning. 
+The database will be composed of a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
+The main partition will be the variables, which means that each variable will be stored in a separate directory.
 If necessary, the data will be partitioned by further variables (as a rule of thumb, each parquet file should not be smaller than 20MB and not bigger than 2GB).
@@
 The models will follow a sequential order.
-The output of a model will serve as a feature to the next model.
+The output of a model will serve as a feature of the next model.
 
@@
 So the outcome will be a binary result (0 = no suppression; 1 = suppression).
-I want that this model to have the minimum inclusion errors for the class "1".
-In other words, I want to avoid, as best as I can, classifying an area with label "1", when the reality is that the area should be label "0".
-To achieve this, the model will be adjusted to present the minimum inclusion error for the class "1", and the probability threshold to classify an observation as class "1" will be a higher value.
+I want this model to have the minimum inclusion errors for class "1".
+In other words, I want to avoid classifying an area with the label "1" when the reality is that it should be labeled "0".
+To achieve this, the model will be adjusted to present the minimum inclusion error for class "1", and the probability threshold to classify an observation as class "1" will be a higher value.
 
 The second model will predict the amount of vegetation suppression that was classified with the label "1" in the previous model.
-The predictions will have to be bounded by the amount of natural vegetation inside the grid cell (a poisson distribution may be adequate to represent this variable).
+The predictions will have to be bounded by the amount of natural vegetation inside the grid cell (a Poisson distribution may be adequate to represent this variable).
 
@@
 
-The fourth model will be actually a set of models.
+The fourth model will be a set of models.
 Each model will be responsible to predict a single environmental or social outcome.
@@
 
-To understand and interpret the predictions made by the models, I will employ a variety of methods to interpret prediction models.
+To understand and interpret the predictions made by the models, I will employ a variety of methods.
 They may include surrogate models, feature interactions, permutation feature importance, counterfactual explanations, and Shapley values.
-These methods are model-agnostic, meaning they can be applied to any type of regression or classification model, regardless of its underlying structure or parameters.
+These methods are model-agnostic, meaning they can be applied to any regression or classification model, regardless of its underlying structure or parameters.
 By using these techniques, I aim to gain a deeper understanding of the relationships between the variables and how they contribute to the predictions.
-This information will help to assess the reliability of the models and the validity of their results.
+This information will enable assessing the reliability of the models and validity of their results.
 
@@
 
-As part of the study, I will not only present the predictions generated by the models, but also perform an in-depth analysis of the models behavior. 
+As part of the study, I will not only present the predictions generated by the models but also perform an in-depth analysis of the model's behavior. 
 This analysis will provide a deeper understanding of the underlying mechanisms that drive the predictions and help to assess their reliability and accuracy.
@@
 
-The main objective of the project is to delve deeper into the reasons behind vegetation removals and to assess their impact on the environment and human well-being. 
-This effort has the potential to provide valuable insights into what can be done to reduce the negative consequences after the vegetation removal. 
+The main objective of the project is to delve deeper into the reasons behind vegetation removals and assess their impact on the environment and human well-being. 
+This effort has the potential to provide valuable insights into what can reduce the negative consequences after vegetation removal. 
 By thoroughly investigating the causes of vegetation removal and its effects, the project aims to contribute to a better understanding of this complex issue and to identify strategies for mitigating its negative impact.

### 2023-03-17 02_get_deforestation.R
Add column for year of deforestation.

@@ -60,7 +60,7 @@ prodes <- rast("data/temp/prodes_brasil_2021.tif")
 
 # TRANSFORM DATA TO BASE GRID ------------------------------------------------
 
-deforastation <-
+deforestation <-
   map_df(
     .x = base_grid$cell_id,
     .f = ~ {
@@ -81,15 +81,29 @@ deforastation <-
         as_tibble() %>%
         select(area)
 
+      total_years <-
+        tibble(
+          year = 2000:2021
+        )
+
       classes %>%
         bind_cols(area) %>%
+        mutate(
+          year = case_when( # Add year of deforestation
+            class < 50 ~ class + 2000,
+            class > 50 & class < 90 ~ class - 40 + 2000,
+            class > 90 ~ NA_integer_
+          )
+        ) %>%
         summarise(
           area = sum(area, na.rm = TRUE),
-          .by = "class"
+          .by = "year"
         ) %>%
-        mutate(cell_id = .x)
+        full_join(total_years, by = join_by(year)) %>%
+        arrange(year) %>%
+        mutate(
+          cell_id = .x # Add id column
+        )
 
     }
   )
-
-

### 2023-03-17 02_get_deforestation.R
Apply mask when calculating pixel area. Implement parallel processing.

@@ -13,6 +13,7 @@ library(terra)
 library(curl)
 library(fs)
 library(glue)
+library(furrr)
 library(tidyverse)
 #
 # CONFLICTS -------------------------------------------------------------------
@@ -30,6 +31,9 @@ data_url <-
     "http://terrabrasilis.dpi.inpe.br/download/dataset/",
     "brasil-prodes/raster/prodes_brasil_2021.zip"
   )
+
+# Configure parallel processing
+plan(multisession, workers = 6)
 
 #
 # DOWNLOAD DATA ---------------------------------------------------------------
@@ -61,11 +65,9 @@ prodes <- rast("data/temp/prodes_brasil_2021.tif")
 # TRANSFORM DATA TO BASE GRID ------------------------------------------------
 
 deforestation <-
-  map_df(
+  map_dfr(
     .x = base_grid$cell_id,
     .f = ~ {
-
-      cat(.x, "\r")
 
       cell <- base_grid %>%
         filter(cell_id == .x)
@@ -77,7 +79,7 @@ deforestation <-
         rename("class" = "prodes_brasil_2021")
 
       area <- cell_subset %>%
-        cellSize() %>%
+        cellSize(mask = TRUE) %>%
         as_tibble() %>%
         select(area)
 

### 2023-03-20 scripts/02_get_deforestation.R
Move file.

@@ -33,24 +33,28 @@ data_url <-
   )
 
 # Configure parallel processing
-plan(multisession, workers = 6)
+plan(multisession, workers = 10)
 
 #
 # DOWNLOAD DATA ---------------------------------------------------------------
 
-dir_create("data/temp/")
+if (!file_exists("data/temp/prodes_brasil_2021.tif")) {
 
-curl_download(
-  url = data_url,
-  destfile = "./data/temp/prodes.zip",
-  quiet = FALSE
-)
+  dir_create("data/temp/")
 
-unzip(
-  zipfile = "./data/temp/prodes.zip",
-  files = "prodes_brasil_2021.tif",
-  exdir = "./data/temp/"
-)
+  curl_download(
+    url = data_url,
+    destfile = "./data/temp/prodes.zip",
+    quiet = FALSE
+  )
+
+  unzip(
+    zipfile = "./data/temp/prodes.zip",
+    files = "prodes_brasil_2021.tif",
+    exdir = "./data/temp/"
+  )
+
+}
 
 # LOAD DATA -------------------------------------------------------------------
 
@@ -58,16 +62,16 @@ base_grid <-
   read_sf("data/base_grid.fgb") %>%
   arrange(cell_id)
 
-prodes <- read_stars("data/temp/prodes_brasil_2021.tif")
-
 prodes <- rast("data/temp/prodes_brasil_2021.tif")
 
 # TRANSFORM DATA TO BASE GRID ------------------------------------------------
 
 deforestation <-
-  map_dfr(
+  map_df(
     .x = base_grid$cell_id,
     .f = ~ {
+
+      cat("Cell ", .x, "\r")
 
       cell <- base_grid %>%
         filter(cell_id == .x)

### 2023-03-20 scripts/02_get_deforestation.R
Remove parallel processing. Add comments.

@@ -13,7 +13,6 @@ library(terra)
 library(curl)
 library(fs)
 library(glue)
-library(furrr)
 library(tidyverse)
 #
 # CONFLICTS -------------------------------------------------------------------
@@ -31,9 +30,6 @@ data_url <-
     "http://terrabrasilis.dpi.inpe.br/download/dataset/",
     "brasil-prodes/raster/prodes_brasil_2021.zip"
   )
-
-# Configure parallel processing
-plan(multisession, workers = 10)
 
 #
 # DOWNLOAD DATA ---------------------------------------------------------------
@@ -68,44 +64,53 @@ prodes <- rast("data/temp/prodes_brasil_2021.tif")
 
 deforestation <-
   map_df(
-    .x = base_grid$cell_id,
+    .x = base_grid$cell_id, # Map function to every grid cell
     .f = ~ {
 
       cat("Cell ", .x, "\r")
 
+      # Filter the cell
       cell <- base_grid %>%
         filter(cell_id == .x)
 
+      # Crop PRODES raster to the cell extent
       cell_subset <- crop(prodes, cell)
 
+      # Get the classes values as a table
       classes <- cell_subset %>%
         as_tibble() %>%
         rename("class" = "prodes_brasil_2021")
 
+      # Calculate the area for each class inside the cell
       area <- cell_subset %>%
         cellSize(mask = TRUE) %>%
         as_tibble() %>%
         select(area)
 
+      # Create table with all years
       total_years <-
         tibble(
           year = 2000:2021
         )
 
+      # Merge classes and areas and process data
       classes %>%
         bind_cols(area) %>%
-        mutate(
+        mutate( # Transform classes to years of deforestation
           year = case_when( # Add year of deforestation
             class < 50 ~ class + 2000,
             class > 50 & class < 90 ~ class - 40 + 2000,
             class > 90 ~ NA_integer_
           )
         ) %>%
-        summarise(
+        summarise( # Get the deforestation are by year
           area = sum(area, na.rm = TRUE),
           .by = "year"
         ) %>%
-        full_join(total_years, by = join_by(year)) %>%
+        full_join( # Add all years to the time series
+          total_years,
+          by = join_by(year)
+        ) %>%
         arrange(year) %>%
         mutate(
           cell_id = .x # Add id column

### 2023-03-20 scripts/02_get_deforestation.R
Add code to save results, clean temporary files. Add script description and notes in the header section.

@@ -1,13 +1,19 @@
 # HEADER ----------------------------------------------------------------------
 #
 # Title:          Get deforestation data
-# Description:
+# Description:    This script downloads and process deforestation data from
+#                 PRODES (http://terrabrasilis.dpi.inpe.br/). The data
+#                 is sliced for each base grid cell, and transformed to
+#                 a table with the deforestation area of each year for each
+#                 cell.
 #
-# Notes:
+# Notes:          This script download PRODES data to your local machine.
+#                 The downloaded files are deleted by the end of the script.
 #
 # LIBRARIES -------------------------------------------------------------------
 #
 library(conflicted)
+library(arrow)
 library(sf)
 library(terra)
 library(curl)
@@ -118,3 +124,17 @@ deforestation <-
 
     }
   )
+
+# SAVE RESULTING DATA ---------------------------------------------------------
+
+# Write deforestation table to parquet file
+write_parquet(
+  x = deforestation,
+  sink = "data/deforestation.parquet",
+  version = "latest"
+)
+
+# CLEAN FILES -----------------------------------------------------------------
+
+# Delete temporary folder with PRODES data
+dir_delete("data/temp/")

### 2023-03-20 manuscript/lct_se_ac.qmd
Small fix.
Change map figure. Rewrite Conclusions.

@@
     page-layout: article
+toc: true
 bibliography: references.bib
@@
 
-library(sf)
-library(geobr)
 library(gt)
@@
 
-The choice of models will depend on a series of tests, accounting the accuracy and adequacy of the model to the theory.
-
 Future projections will serve as a bridge to discuss public policy planning to mitigate the negative impacts of native vegetation suppression in the Amazon and Cerrado.
@@
 
-```{r}
-#| label: grid-map-figure
-#| echo: false
-#| message: false
-
-biomes <- read_biomes(showProgress = FALSE) %>%
-  filter(name_biome %in% c("Amazônia", "Cerrado")) %>%
-  st_make_valid()
-
-grid <- 
-  st_make_grid(biomes, cellsize = 0.2) %>%
-  st_as_sf() %>%
-  st_filter(biomes, .predicate = st_intersects)
-
-ggplot() +
-  geom_sf(data = biomes) +
-  geom_sf(data = grid, fill = "transparent") +
-  theme_void()
-
-```
+![Representation of the spatial grid that will be used to store the data from different sources.](figs/grid_cells.png)
 
@@
 
-The data will be stored in a nested directories structured database with hive-style partitioning. 
+The data will be stored in a nested directories database with hive-style partitioning. 
 The database will be composed of a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
@@
 
-The main objective of the project is to delve deeper into the reasons behind vegetation removals and assess their impact on the environment and human well-being. 
-This effort has the potential to provide valuable insights into what can reduce the negative consequences after vegetation removal. 
-By thoroughly investigating the causes of vegetation removal and its effects, the project aims to contribute to a better understanding of this complex issue and to identify strategies for mitigating its negative impact.
-The end goal is to ensure that future vegetation removal is carried out in a way that minimizes harm to the environment and supports the well-being of people who depend on it.
+The final outcome of this project is expected to provide answers to the following questions as concluding remarks:
+
+- How suitable were the models to represent the studied phenomena?
+
+The final remarks should summarize the potential of utilizing observed data and statistical models to estimate the causes and impacts of deforestation, as also explore the limitations of this method.
+
+- What are the implications of the results to the development of public policies in the Amazon and Cerrado biomes?
+
+Assuming that the models were suitable for representing the phenomena, the concluding remarks will summarize how the results can inform important variables that need to be taken into account for the development of public policies.
+Spatialization may also prove useful by providing regions that are more suitable for different kinds of strategies to mitigate deforestation and its impacts.
 

### 2023-03-21 scripts/02_get_deforestation.R
Small fix.

@@ -66,7 +66,7 @@ base_grid <-
 
 prodes <- rast("data/temp/prodes_brasil_2021.tif")
 
-# TRANSFORM DATA TO BASE GRID ------------------------------------------------
+# TRANSFORM DATA TO BASE GRID -------------------------------------------------
 
 deforestation <-
   map_df(

### 2023-03-21 03_get_uc.R
Add code to download and process conservation units data.

@@ -1,0 +1,106 @@
+# HEADER ----------------------------------------------------------------------
+#
+# Title:          Get protected areas data
+# Description:
+#
+# Notes:
+#
+# LIBRARIES -------------------------------------------------------------------
+#
+library(conflicted)
+library(arrow)
+library(sf)
+library(geobr)
+library(janitor)
+library(units)
+library(glue)
+library(tidyverse)
+#
+# CONFLICTS -------------------------------------------------------------------
+#
+
+conflicts_prefer(dplyr::filter)
+
+#
+# OPTIONS ---------------------------------------------------------------------
+#
+
+#
+# LOAD DATA -------------------------------------------------------------------
+
+base_grid <-
+  read_sf("data/base_grid.fgb") %>%
+  arrange(cell_id)
+
+# Get UC data from geobr
+c_units <-
+  read_conservation_units() %>%
+  st_make_valid()
+
+# TRANSFORM DATA TO BASE GRID -------------------------------------------------
+
+# Select UC columns
+c_units <- c_units %>%
+  select(
+    code_conservation_unit, category, group, government_level,
+    creation_year, geom
+  )
+
+st_agr(c_units) = "constant"
+
+st_agr(base_grid) = "constant"
+
+uc <-
+  map_df(
+    .x = base_grid$cell_id, # Map function to every grid cell
+    .f = ~ {
+
+      cat("Cell ", .x, "\r")
+
+      # Filter the cell
+      cell <- base_grid %>%
+        filter(cell_id == .x)
+
+      cell_units <- c_units %>%
+        st_intersection(cell)
+
+      # Create table with all years
+      total_years <-
+        tibble(
+          year = 2000:2021
+        )
+
+      if (nrow(cell_units) == 0) {
+
+        cell_units <- tibble_row(
+          !!!names(cell_units)
+        ) %>%
+          clean_names() %>%
+          mutate(
+            across(.cols = everything(), ~ NA),
+            uc_area = set_units(NA_integer_, "m^2", mode = "standard"),
+            cell_id = .x
+          ) %>%
+          select(!geom) %>%
+          bind_cols(total_years)
+
+      } else {
+
+        cell_units <- cell_units %>%
+          mutate(uc_area = st_area(.)) %>%
+          as_tibble() %>%
+          select(!geom) %>%
+          mutate(year = as.numeric(creation_year)) %>%
+          full_join(
+            total_years,
+            by = join_by(year)
[…]

### 2023-03-22 scripts/03_get_uc.R
Move script file.

@@ -39,18 +39,22 @@ c_units <-
 
 # TRANSFORM DATA TO BASE GRID -------------------------------------------------
 
-# Select UC columns
+# Select UC columns and fix dates
 c_units <- c_units %>%
   select(
     code_conservation_unit, category, group, government_level,
     creation_year, geom
+  ) %>%
+  mutate(
+    creation_year = str_sub(creation_year, start = -4),
+    creation_year = as.numeric(creation_year)
   )
 
 st_agr(c_units) = "constant"
 
 st_agr(base_grid) = "constant"
 
-uc <-
+uc_grid <-
   map_df(
     .x = base_grid$cell_id, # Map function to every grid cell
     .f = ~ {
@@ -90,7 +94,7 @@ uc <-
           mutate(uc_area = st_area(.)) %>%
           as_tibble() %>%
           select(!geom) %>%
-          mutate(year = as.numeric(creation_year)) %>%
+          mutate(year = creation_year) %>%
           full_join(
             total_years,
             by = join_by(year)
@@ -104,3 +108,12 @@ uc <-
 
     }
   )
+
+# SAVE RESULTING DATA ---------------------------------------------------------
+
+# Write deforestation table to parquet file
+write_parquet(
+  x = uc_grid,
+  sink = "data/uc.parquet",
+  version = "latest"
+)

### 2023-03-24 R/create_grid.R
Transform repo to a R package.

@@ -1,0 +1,33 @@
+create_grid <- function(resolution, full_cells) {
+
+  # Load biomes limit
+  biomes <-
+    read_biomes(
+      year = 2019,
+      simplified = TRUE, # Biome limits are simplified (topology preserved)
+      showProgress = FALSE
+    ) %>%
+    filter(name_biome %in% c("Amazônia", "Cerrado"))
+
+  # Create grid based on polygons
+  grid <-
+    st_make_grid(
+      x = biomes,
+      cellsize = resolution # Resolution of the grid cell
+    ) %>%
+    st_as_sf() %>%
+    st_join(
+      y = biomes,
+      left = FALSE,
+      # Choose filter function based on option above
+      join = if (full_cells) {st_within} else {st_intersects}
+    ) %>%
+    select(name_biome, geometry) %>%
+    mutate(
+      cell_id = row_number(),
+      cell_area = st_area(geometry)
+    )
+
+  return(grid)
+
+}

### 2023-03-24 scripts/01_set_grid.R

@@ -1,95 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:          Create project grid
-# Description:    This script creates a grid that will be used for all
-#                 data in this project
-#
-# Notes:
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(conflicted)
-library(sf)
-library(geobr)
-library(tidyverse)
-#
-# CONFLICTS -------------------------------------------------------------------
-#
-
-conflicts_prefer(dplyr::filter)
-
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-
-# Size of the grid cell in degrees
-resolution <- 0.2
-
-# Create grid with cells that are fully within the biomes?
-full_cells <- TRUE
-# If TRUE, st_within is called as predicate for spatial filter
-# If FALSE, st_intersects is called as predicate for spatial filter
-
-#
-# LOAD DATA -------------------------------------------------------------------
-
-# Load biomes limit
-biomes <-
-  read_biomes(
-    year = 2019,
-    simplified = TRUE, # Biome limits are simplified (topology preserved)
-    showProgress = FALSE
-  ) %>%
-  filter(name_biome %in% c("Amazônia", "Cerrado"))
-
-# CREATE AND SAVE GRID --------------------------------------------------------
-
-# Create grid based on biomes polygons
-grid <-
-  st_make_grid(
-    x = biomes,
-    cellsize = resolution # Resolution of the grid cell (check options above)
-  ) %>%
-  st_as_sf() %>%
-  st_filter(
-    y = biomes,
-    # Choose filter function based on option above
-    .predicate = if (full_cells) {st_within} else {st_intersects}
-  ) %>%
-  rename(cell = x) %>%
-  mutate(cell_id = row_number())
-
-# Save grid polygons as FlatGeobuf file
-write_sf(
-  obj = grid,
-  dsn = "./data/base_grid.fgb",
-  driver = "FlatGeobuf",
-  append = FALSE,
-  delete_dsn = TRUE
-)
-
-# CREATE AND SAVE PLOT --------------------------------------------------------
-
-# Plot grid and biome limits
-grid_plot <- ggplot() +
-  geom_sf(
-    data = biomes,
-    fill = "transparent"
-  ) +
-  geom_sf(
-    data = grid,
-    fill = "transparent"
-  ) +
-  theme_void() +
[…]

### 2023-03-24 scripts/02_get_deforestation.R

@@ -1,140 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:          Get deforestation data
-# Description:    This script downloads and process deforestation data from
-#                 PRODES (http://terrabrasilis.dpi.inpe.br/). The data
-#                 is sliced for each base grid cell, and transformed to
-#                 a table with the deforestation area of each year for each
-#                 cell.
-#
-# Notes:          This script download PRODES data to your local machine.
-#                 The downloaded files are deleted by the end of the script.
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(conflicted)
-library(arrow)
-library(sf)
-library(terra)
-library(curl)
-library(fs)
-library(glue)
-library(tidyverse)
-#
-# CONFLICTS -------------------------------------------------------------------
-#
-
-conflicts_prefer(dplyr::filter)
-
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-
-# Data URL
-data_url <-
-  glue(
-    "http://terrabrasilis.dpi.inpe.br/download/dataset/",
-    "brasil-prodes/raster/prodes_brasil_2021.zip"
-  )
-
-#
-# DOWNLOAD DATA ---------------------------------------------------------------
-
-if (!file_exists("data/temp/prodes_brasil_2021.tif")) {
-
-  dir_create("data/temp/")
-
-  curl_download(
-    url = data_url,
-    destfile = "./data/temp/prodes.zip",
-    quiet = FALSE
-  )
-
-  unzip(
-    zipfile = "./data/temp/prodes.zip",
-    files = "prodes_brasil_2021.tif",
-    exdir = "./data/temp/"
-  )
-
-}
-
-# LOAD DATA -------------------------------------------------------------------
-
-base_grid <-
-  read_sf("data/base_grid.fgb") %>%
-  arrange(cell_id)
-
-prodes <- rast("data/temp/prodes_brasil_2021.tif")
-
-# TRANSFORM DATA TO BASE GRID -------------------------------------------------
-
-deforestation <-
-  map_df(
-    .x = base_grid$cell_id, # Map function to every grid cell
-    .f = ~ {
-
-      cat("Cell ", .x, "\r")
-
-      # Filter the cell
-      cell <- base_grid %>%
-        filter(cell_id == .x)
-
-      # Crop PRODES raster to the cell extent
-      cell_subset <- crop(prodes, cell)
-
-      # Get the classes values as a table
-      classes <- cell_subset %>%
-        as_tibble() %>%
[…]

### 2023-03-24 scripts/03_get_uc.R

@@ -1,119 +1,0 @@
-# HEADER ----------------------------------------------------------------------
-#
-# Title:          Get protected areas data
-# Description:
-#
-# Notes:
-#
-# LIBRARIES -------------------------------------------------------------------
-#
-library(conflicted)
-library(arrow)
-library(sf)
-library(geobr)
-library(janitor)
-library(units)
-library(glue)
-library(tidyverse)
-#
-# CONFLICTS -------------------------------------------------------------------
-#
-
-conflicts_prefer(dplyr::filter)
-
-#
-# OPTIONS ---------------------------------------------------------------------
-#
-
-#
-# LOAD DATA -------------------------------------------------------------------
-
-base_grid <-
-  read_sf("data/base_grid.fgb") %>%
-  arrange(cell_id)
-
-# Get UC data from geobr
-c_units <-
-  read_conservation_units() %>%
-  st_make_valid()
-
-# TRANSFORM DATA TO BASE GRID -------------------------------------------------
-
-# Select UC columns and fix dates
-c_units <- c_units %>%
-  select(
-    code_conservation_unit, category, group, government_level,
-    creation_year, geom
-  ) %>%
-  mutate(
-    creation_year = str_sub(creation_year, start = -4),
-    creation_year = as.numeric(creation_year)
-  )
-
-st_agr(c_units) = "constant"
-
-st_agr(base_grid) = "constant"
-
-uc_grid <-
-  map_df(
-    .x = base_grid$cell_id, # Map function to every grid cell
-    .f = ~ {
-
-      cat("Cell ", .x, "\r")
-
-      # Filter the cell
-      cell <- base_grid %>%
-        filter(cell_id == .x)
-
-      cell_units <- c_units %>%
-        st_intersection(cell)
-
-      # Create table with all years
-      total_years <-
-        tibble(
-          year = 2000:2021
-        )
-
-      if (nrow(cell_units) == 0) {
-
-        cell_units <- tibble_row(
-          !!!names(cell_units)
-        ) %>%
-          clean_names() %>%
-          mutate(
-            across(.cols = everything(), ~ NA),
-            uc_area = set_units(NA_integer_, "m^2", mode = "standard"),
-            cell_id = .x
-          ) %>%
-          select(!geom) %>%
-          bind_cols(total_years)
-
-      } else {
-
-        cell_units <- cell_units %>%
-          mutate(uc_area = st_area(.)) %>%
-          as_tibble() %>%
[…]

### 2023-03-24 README.Rmd
Update documentation.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of TICA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hugotseixas/tica")
```

### 2023-03-24 R/create_grid.R
Add function to create base grid for the model.

@@ -1,31 +1,41 @@
+#' Create base grid for TICA
+#'
+#' @param resolution Set the resolution of the grid in degrees.
+#' @param full_cells Choose if cells should completely inside the biomes.
+#'
+#' @return A tibble.
+#' @export
+#'
+#' @examples
+#' base_grid <- create_grid(resolution = 0.2, full_cells = TRUE)
 create_grid <- function(resolution, full_cells) {
 
   # Load biomes limit
   biomes <-
-    read_biomes(
+    geobr::read_biomes(
       year = 2019,
       simplified = TRUE, # Biome limits are simplified (topology preserved)
       showProgress = FALSE
-    ) %>%
-    filter(name_biome %in% c("Amazônia", "Cerrado"))
+    ) |>
+    dplyr::filter(code_biome %in% c(1, 3))
 
   # Create grid based on polygons
   grid <-
-    st_make_grid(
+    sf::st_make_grid(
       x = biomes,
       cellsize = resolution # Resolution of the grid cell
-    ) %>%
-    st_as_sf() %>%
-    st_join(
+    ) |>
+    sf::st_as_sf() |>
+    sf::st_join(
       y = biomes,
       left = FALSE,
       # Choose filter function based on option above
-      join = if (full_cells) {st_within} else {st_intersects}
-    ) %>%
-    select(name_biome, geometry) %>%
-    mutate(
-      cell_id = row_number(),
-      cell_area = st_area(geometry)
+      join = if (full_cells) { sf::st_within } else { sf::st_intersects }
+    ) |>
+    dplyr::select(name_biome, geometry) |>
+    dplyr::mutate(
+      cell_id = dplyr::row_number(),
+      cell_area = sf::st_area(geometry)
     )
 
   return(grid)

### 2023-03-24 README.Rmd
Update readme.

@@
 
-# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon
+# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon <a href="https://hugotseixas.com/en/tica/"><img src="man/figures/logo.png" align="right" height="138" /></a>
 
@@
 <!-- badges: end -->
+
+## Overview
+
+TICA is a model being develop to estimate deforestation, land use transitions, and their impact on social and environmental aspects of the Cerrado and Amazônia biomes in Brazil.
+This model is part of an effort to develop an interdisciplinary approach to analyse these phenomena.
 

### 2023-03-24 README.Rmd
Update readme.

@@
   comment = "#>",
-  fig.path = "man/figures/README-",
+  fig.path = "/man/figures/README-",
   out.width = "100%"
@@
 
-# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon <a href="https://hugotseixas.com/en/tica/"><img src="man/figures/logo.png" align="right" height="138" /></a>
+# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon <a href="https://hugotseixas.com/en/tica/"><img src="/man/figures/logo.png" align="right" height="138" /></a>
 

### 2023-03-27 R/create_grid.R
Small code template changes.

@@ -8,6 +8,7 @@
 #'
 #' @examples
 #' base_grid <- create_grid(resolution = 0.2, full_cells = TRUE)
+#'
 create_grid <- function(resolution, full_cells) {
 
   # Load biomes limit
@@ -38,6 +39,6 @@ create_grid <- function(resolution, full_cells) {
       cell_area = sf::st_area(geometry)
     )
 
-  return(grid)
+  base::return(grid)
 
 }

### 2023-03-27 R/process_conservation_units.R
Add function to process conservation units data.

@@ -1,0 +1,110 @@
+#' Process conservation units data to base grid
+#'
+#' @param base_grid_path Path to the base grid file
+#' @param timespan Set the years for the data in the base grid
+#'
+#' @return A tibble
+#' @export
+#'
+#' @examples
+#' \dontrun{
+#'   uc_grid <- process_conservation_units("./data/base_grid.fgb", 1985:2021)
+#' }
+#'
+process_conservation_units <- function(base_grid_path, timespan) {
+
+  base_grid <-
+    sf::read_sf(base_grid_path) |>
+    dplyr::arrange(cell_id)
+
+  cell_list <- base_grid |>
+    dplyr::pull(cell_id)
+
+  conservation_units <-
+    geobr::read_conservation_units(showProgress = FALSE) |>
+    sf::st_make_valid() |>
+    dplyr::select( # Select variables
+      code_conservation_unit, category, group,
+      government_level, creation_year, geom
+    ) |>
+    dplyr::mutate( # Fix dates
+      creation_year = stringr::str_sub(creation_year, start = -4),
+      creation_year = base::as.numeric(creation_year)
+    )
+
+  sf::st_agr(conservation_units) = "constant"
+
+  sf::st_agr(base_grid) = "constant"
+
+  uc_grid <-
+    purrr::map_df(
+      .x = cell_list, # Map function to every grid cell
+      .f = ~ {
+
+        cat(
+          "Progress: ",
+          round(.x/base::length(cell_list) * 100),
+          "%",
+          "\r"
+        )
+
+        # Filter the cell
+        cell <- base_grid |>
+          dplyr::filter(cell_id == .x)
+
+        cell_units <- conservation_units |>
+          sf::st_intersection(cell)
+
+        # Create table with all years
+        total_years <-
+          tibble::tibble(
+            year = timespan
+          )
+
+        if (base::nrow(cell_units) == 0) {
+
+          cell_units <-
+            tibble_row(
+              !!!base::names(cell_units)
+            ) |>
+            janitor::clean_names() |>
+            dplyr::mutate(
+              cell_area = cell$cell_area,
+              name_biome = cell$name_biome,
+              cell_id = cell$cell_id,
+              dplyr::across(code_conservation_unit:creation_year, ~ NA_real_),
+              uc_area = units::set_units(
+                0,
+                "m^2",
+                mode = "standard"
+              )
+            ) |>
+            dplyr::select(!geom) |>
+            dplyr::bind_cols(total_years)
[…]

### 2023-03-27 R/process_conservation_units.R
Remove unnecessary columns. Fix column types error.

@@ -8,14 +8,15 @@
 #'
 #' @examples
 #' \dontrun{
-#'   uc_grid <- process_conservation_units("./data/base_grid.fgb", 1985:2021)
+#'   uc_grid <- process_conservation_units("./inst/base_grid.fgb", 1985:2021)
 #' }
 #'
 process_conservation_units <- function(base_grid_path, timespan) {
 
   base_grid <-
     sf::read_sf(base_grid_path) |>
-    dplyr::arrange(cell_id)
+    dplyr::arrange(cell_id) |>
+    dplyr::select(cell_id, geometry)
 
   cell_list <- base_grid |>
     dplyr::pull(cell_id)
@@ -24,8 +25,8 @@ process_conservation_units <- function(base_grid_path, timespan) {
     geobr::read_conservation_units(showProgress = FALSE) |>
     sf::st_make_valid() |>
     dplyr::select( # Select variables
-      code_conservation_unit, category, group,
-      government_level, creation_year, geom
+      category, group, government_level,
+      creation_year, geom
     ) |>
     dplyr::mutate( # Fix dates
       creation_year = stringr::str_sub(creation_year, start = -4),
@@ -53,7 +54,8 @@ process_conservation_units <- function(base_grid_path, timespan) {
           dplyr::filter(cell_id == .x)
 
         cell_units <- conservation_units |>
-          sf::st_intersection(cell)
+          sf::st_intersection(cell) |>
+          dplyr::relocate(cell_id)
 
         # Create table with all years
         total_years <-
@@ -64,15 +66,17 @@ process_conservation_units <- function(base_grid_path, timespan) {
         if (base::nrow(cell_units) == 0) {
 
           cell_units <-
-            tibble_row(
+            tibble::tibble_row(
               !!!base::names(cell_units)
             ) |>
             janitor::clean_names() |>
             dplyr::mutate(
-              cell_area = cell$cell_area,
-              name_biome = cell$name_biome,
               cell_id = cell$cell_id,
-              dplyr::across(code_conservation_unit:creation_year, ~ NA_real_),
+              dplyr::across(
+                category:government_level,
+                ~ NA_character_
+              ),
+              creation_year = NA_integer_,
               uc_area = units::set_units(
                 0,
                 "m^2",
@@ -88,16 +92,22 @@ process_conservation_units <- function(base_grid_path, timespan) {
             dplyr::mutate(uc_area = sf::st_area(geom)) |>
             tibble::as_tibble() |>
             dplyr::select(!geom) |>
[…]
